---
title: "S-08 Earned Credit hours"
author: "Craig Demke"
date: "`r Sys.Date()`"
output: html_document
---

```{r set global chunks, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE
)
```

```{r load libraries}
library(tidyverse)
library(datasets)
library(plotly)
library(gt)
library(glue)
library(stringr)
library(DT)
library(purrr)
library(here)
```
### This is part of the Student Course Data  Element: SC-08
*   ELEMENT NAME: Credit Hours Earned 
*   FIELD NAME: SC_EARNED_CR 
*   FIELD FORMAT: Numeric (3,1) 
*   DEFINITION: Credit hours earned by the student for the course. This field is for credit courses  only.  
COMMENTS: ***This field needs to be populated for end of term extract file.***

### This data is found in Edify from export.student_section_version.earned_credits and student_section_version.version_desc
```{}
--S-08
SELECT DISTINCT(student_id),
       earned_credits,
       version_desc
FROM export.student_section_version
WHERE term_id = '202140'
--AND earned_credits > '0'
ORDER BY student_id
LIMIT 10;
```


### Create fake data that matches the version description and earned credits found in Edify

```{r}
sc_08_earned_credits_test_df <- tibble(
  version_desc = sample(c("Census", "Current", "End of Term"), 10, replace = TRUE),
  earned_credits = sample(1:120, 10, replace = TRUE)
  
)
   

DT::datatable(sc_08_earned_credits_test_df, rownames=FALSE)
```

### Now let's see if we can pull in real data

```{r}
### We pull the data we want from the report database REPT 

sc_08_earned_credits_real_df <- utHelpR::get_data_from_sql_file(file_name="sc_08.sql",
                                               dsn="edify",
                                               context="sandbox")

# display data pulled in table
DT::datatable(sc_08_earned_credits_real_df, rownames=FALSE)
```


### Here is the R script

The first thing I need to do is to figure out how to

```{r}

change_sc_08_earned_credits_df <- sc_08_earned_credits_test_df %>%
    mutate(sc_earned_cr = ifelse(version_desc == "End of Term", earned_credits, "" )) %>%
    mutate(s_08 = sc_earned_cr)
  
DT::datatable(change_sc_08_earned_credits_df, rownames=FALSE)

```

### Making a function

```{r}
  
format_sc_08_earned_credits <- function(input_df, with_intermediates=FALSE) {

  output_df <- input_df %>%
    mutate(sc_earned_cr = ifelse(version_desc == "End of Term", earned_credits, "" )) %>%
    mutate(s_08 = sc_earned_cr)

    if (!with_intermediates) {
      output_df <- output_df %>%

        select(-c(sc_earned_cr))
    }

  return(output_df)

  
}
```
### Choose which data frame you want pass through the function 

sc_08_earned_credits_test_df for the fake data set
```{r}
DT::datatable(format_sc_08_earned_credits(sc_08_earned_credits_test_df), rownames=FALSE)
```

sc_08_earned_credits_real_df for the real data
```{r}
DT::datatable(format_sc_08_earned_credits(sc_08_earned_credits_real_df), rownames=FALSE)
```

