---
title: "SC-12 Student Type Code"
author: "Craig Demke"
date: '2022-07-11'
output: html_document
---


```{r set global chunks, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE
)
```

```{r load libraries}
library(tidyverse)
library(datasets)
library(plotly)
library(gt)
library(glue)
library(stringr)
library(DT)
library(purrr)
library(here)
```
### This is part of the Student Courses Data Element: SC-12
* ELEMENT NAME: Student Type Code 
* FIELD NAME: SC_STUDENT_TYPE 
* FIELD FORMAT: Varchar, 2 Characters 
* DEFINITION: The specific code which would identify students according to special  registration/tuition status. Average Daily Membership (ADM) is a count of Utah public education  students that is taken at different times of the year to satisfy local, state, and federal data collection  needs and also to ensure that school districts are adequately funded, according to student population.  The Concurrent Enrollment Master List is a list of college-level courses which have been approved by  the Utah State Board of Education for Concurrent Enrollment. 

### This data is found in Edify from 
```{}

```


### Create fake data that matches this.

```{r}
sc_12_student_type_code_test_df <- tibble(
  latest_student_type = sample(c("H"), 10, replace = TRUE),
  #section_number = sample(c("12345"), 10, replace = TRUE),
  #subject_code = sample(c("PSY"), 10, replace = TRUE),
  #course_id = sample(c("PSY-1010"), 10, replace = TRUE),
  high_school_code = sample(c("123456", "234567", "459500", "459600", "459998", "969999", "459150", "459300", "459200"), 10, replace = TRUE),
  season = sample(c("spring"), 10, replace = TRUE),
  budget_code = sample(c("SF", "BC", "BA"), 10, replace = TRUE),
  edify_field = sample(c("conc", ""), 10, replace = TRUE)
)

DT::datatable(sc_12_student_type_code_test_df, rownames=FALSE)
```

### Now let's see if we can pull in real data

```{r}
### We pull the data we want from the report database REPT 

sc_12_student_type_code_real_df <- utHelpR::get_data_from_sql_file(file_name="sc_12_student_type_code.sql",
                                               dsn="edify",
                                               context="sandbox")

# display data pulled in table
DT::datatable(sc_12_student_type_code_real_df, rownames=FALSE)
```


### Here is the R script

The first thing I need to do is to figure out how to

```{r}

option1 <- sc_12_student_type_code_test_df %>%
mutate( student_type_code = if_else(latest_student_type == "H" & (high_school_code == "459500" |
                               high_school_code == "459600"|
                               high_school_code == "459998"|
                               high_school_code == "969999"|
                               high_school_code == "459150"|
                               high_school_code == "459300"|
                               high_school_code == "459200"), "EC",
                         if_else(latest_student_type == "H" & (budget_code == "BC" | budget_code == "SF") & edify_field == "conc", "CC",
                         if_else(latest_student_type == "H" & (budget_code == "BC" | budget_code == "SF") & edify_field != "conc", "DC", "")))
)

option2 <- sc_12_student_type_code_test_df %>%
mutate( student_type_code = if_else(latest_student_type == "H" & (budget_code != "BC" & budget_code != "SF" ), "EC",
                         if_else(latest_student_type == "H" & (budget_code == "BC" | budget_code == "SF") & edify_field == "conc", "CC",
                         if_else(latest_student_type == "H" & (budget_code == "BC" | budget_code == "SF") & edify_field != "conc", "DC", "")))
)
    
    #grep("M", high_school_code) = TRUE ~ "7"
    


DT::datatable(option2, rownames=FALSE)



```

### Making a function

```{r}
  
format_sc_12_student_type_code <- function(input_df, with_intermediates=FALSE) {

  output_df <- input_df %>%
  mutate( student_type_code = if_else(latest_student_type == "H" & (budget_code != "BC" & budget_code != "SF" ), "EC",
                         if_else(latest_student_type == "H" & (budget_code == "BC" | budget_code == "SF") & edify_field == "conc", "CC",
                         if_else(latest_student_type == "H" & (budget_code == "BC" | budget_code == "SF") & edify_field != "conc", "DC", "")))
) %>% 
    mutate(sc_12 = student_type_code)

    if (!with_intermediates) {
      output_df <- output_df %>%
        # Remove fields used for intermediate calculations
        select( -c(sc_12) )
    }

  return(output_df)

  
}
```
### Choose which data frame you want pass through the function 

sc_12_student_type_code_test_df for the fake data set
```{r}
DT::datatable(format_sc_12_student_type_code(sc_12_student_type_code_test_df), rownames=FALSE)
```

sc_12_student_type_code_real_df for the real data
```{r}
DT::datatable(format_sc_12_student_type_code(sc_12_student_type_code_real_df), rownames=FALSE)
```

