---
title: "B-15 Auxiliary Building"
author: "Craig Demke"
date: "`r Sys.Date()`"
output: html_document
---

```{r set global chunks, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE
)
```

```{r load libraries}
library(tidyverse)
library(datasets)
library(plotly)
library(gt)
library(glue)
library(stringr)
library(DT)
library(purrr)
library(here)
```
### This is part of the 
* 

### This data is found in Edify from 
```{}

```


### Create fake data that matches this.

```{r}
b_15_aux_building_test_df <- tibble(
  building_auxiliary = sample(c("Y", "N"), 10, replace = TRUE)
) 
   

DT::datatable(b_15_aux_building_test_df, rownames=FALSE)
```

### Now let's see if we can pull in real data

```{r}
### We pull the data we want from the report database REPT 

b_15_aux_building_real_df <- utHelpR::get_data_from_sql_file(file_name="b_15.sql",
                                               dsn="edify",
                                               context="sandbox")

# display data pulled in table
DT::datatable(b_15_aux_building_real_df, rownames=FALSE)
```


### Here is the R script

The first thing I need to do is to figure out how to convert Y to A and code the rest N

```{r}

change_b_15_aux_building_df <- b_15_aux_building_test_df %>%
       mutate(b_aux = case_when(
     building_auxiliary == "Y" ~ "A",
     TRUE ~ "N"))

DT::datatable(change_b_15_aux_building_df, rownames=FALSE)

```

### Making a function

```{r}
  
format_b_15_aux_building <- function(input_df, with_intermediates=FALSE) {

  output_df <- input_df %>%
   mutate(b_aux = case_when(
     building_auxiliary == "Y" ~ "A",
     TRUE ~ "N")) %>%
    mutate(b_15 = b_aux)

    if (!with_intermediates) {
      output_df <- output_df %>%
        select( -c(b_aux))
    }

  return(output_df)

  
}
```
### Choose which data frame you want pass through the function 

b_15_aux_building_test_df for the fake data set
```{r}
DT::datatable(format_b_15_aux_building(b_15_aux_building_test_df), rownames=FALSE)
```

b_15_aux_building_real_df for the real data
```{r}
DT::datatable(format_b_15_aux_building(b_15_aux_building_real_df), rownames=FALSE)

  #dt_test <- format_b_15_aux_building(b_15_aux_building_real_df)
#view(dt_test)
```

