---
title: "C-02"
author: "Craig Demke"
date: '2022-06-15'
output: html_document
---

---
```{r set global chunks, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE
)
```

```{r load libraries}
library(tidyverse)
library(datasets)
library(plotly)
library(gt)
library(glue)
library(stringr)
library(DT)
library(purrr)
```
## This is part of the Course Data Submission to USHE Element C-17
ELEMENT NAME: Section Days 1 
FIELD NAME: C_DAYS 
FIELD FORMAT: Varchar, 7 Characters 
With one position for each day of week, starting with Monday. 

## This data is found in Edify from export.section_schedule table
```{}

```


### Create fake data that matches this.

```{r}
year_term_extract_test_df <- tibble(
  academic_year_code = (2022),
  season = sample(c("Summer", "Fall", "Spring"), 10, replace = TRUE),
  version_id = sample(c(2, 3), 10, replace = TRUE)
) 

DT::datatable(year_term_extract_test_df, rownames=FALSE)
```

### Now let's see if we can pull in real data

```{r}
### We pull the data we want from Edify
#library(here)
#source(here::here("R", "data_io_util.R"))

#real_c17_df <- get_data_from_sql_file(file_name="c_02.sql",
 #                            dsn="edify")
# display data pulled in table
#DT::datatable(real_c_02_df, rownames=FALSE)
```

## ## Here is the R script

The first thing I need to do is to figure out how to
```{r}
# Adding conditional logic to determine c_term_id

change_year_term_extract <- year_term_extract_test_df %>%
  mutate(t_format = case_when(
    season == "Summer" ~ '1',
    season == "Fall" ~ '2',
    season == 'Spring' ~ '3',
    TRUE ~ "mistake")) %>% 
  mutate(v_format = case_when(
    version_id == '2' ~ '3',
    version_id == '3' ~ 'E',
    TRUE ~ "mistake"))

change_year_term_extract$"year_term_extract" = paste(change_year_term_extract$academic_year_code,
                                        change_year_term_extract$t_format,
                                        change_year_term_extract$v_format)

change_year_term_extract$Remove_all_space <- gsub('\\s+', '', change_year_term_extract$"year_term_extract")

DT::datatable(change_year_term_extract)

```

Now we write the function
```{r}
format_ushe_year_term_extract <- function(input_df) {
  
  output_df <- input_df %>%
  mutate(t_format = case_when(
    season == "Summer" ~ '1',
    season == "Fall" ~ '2',
    season == 'Spring' ~ '3',
    TRUE ~ "mistake")) %>% 
  mutate(v_format = case_when(
    version_id == '2' ~ '3',
    version_id == '3' ~ 'E',
    TRUE ~ "mistake"))

output_df$"year_term_extract" = paste(output_df$academic_year_code,
                                        output_df$t_format,
                                        output_df$v_format)

output_df$Remove_all_space <- gsub('\\s+', '', output_df$"year_term_extract")

return(output_df)
}
```
## Choose which data frame you want pass through the function 

 for the fake data set
```{r}
DT::datatable(format_ushe_year_term_extract(year_term_extract_test_df))
```

--- for the real data
```{r}
#DT::datatable(format_ushe_year_term_extract(place_holder))
```

