---
title: "C_14_credit_indicator"
author: "Craig Demke"
date: '2022-06-21'
output: html_document
---
---
title: "c_14_credit_indicator"
output: html_document
date: '2022-06-01'
---

```{r set global chunks, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE
)
```

```{r load libraries}
library(tidyverse)
library(datasets)
library(plotly)
library(gt)
library(glue)
library(stringr)
library(DT)
library(purrr)
library(here)
```
## This is part of the Course Data
ELEMENT NAME: Credit Indicator 
FIELD NAME: C_CREDIT_IND 
FIELD FORMAT: Varchar, 1 Character 
DEFINITION: A code indicating whether the course is offered for credit or not. 

## This data is found in Edify from export.course, course_level_id.
```{}
SELECT DISTINCT (course_level_id)
FROM course;
```


### Create fake data that matches this.

```{r}
c_14_credit_indicator_test_df <- tibble(
  course_reference_number = sample(1:99999, 10),
  course_level_id = sample(c("CE", "UG", "GR", "NC", NULL), 10, replace = TRUE))

DT::datatable(c_14_credit_indicator_test_df, rownames=FALSE)
```

### Now let's see if we can pull in real data

```{r}
### We pull the data we want from the report database REPT 
library(here)
source(here::here("R", "data_io_util.R"))

c_14_credit_indicator_real_df <- get_data_from_sql_file(file_name="c_14.sql",
                             dsn="edify")
# display data pulled in table
DT::datatable(c_14_credit_indicator_real_df, rownames=FALSE)
```


## Here is the R script

The first thing I need to do is to figure out how to

```{r}

change_c_14_credit_indicator_df <- c_14_credit_indicator_test_df %>%
   mutate(c_credit_ind = case_when(
  course_level_id == "CE" ~ 'N',
  course_level_id == "UG" ~ 'C',
  course_level_id == "GR" ~ 'C',
  course_level_id == "NC" ~ 'N',
  TRUE ~ 'error'))


DT::datatable(change_c_14_credit_indicator_df, rownames=FALSE)



```

## Making a function

```{r}

format_c_14_credit_indicator <- function(input_df) {
  
  output_df <- input_df %>%  
    mutate(c_credit_ind = case_when(
    course_level_id == "CE" ~ 'N',
    course_level_id == "UG" ~ 'C',
    course_level_id == "GR" ~ 'C',
    course_level_id == "NC" ~ 'N',
    TRUE ~ 'error')) # what do we want to put for null?
  
  output_df <- output_df %>% 

  
  return(output_df)
  
}
```
## Choose which data frame you want pass through the function 

c_14_credit_indicator_test_df for the fake data set
```{r}
DT::datatable(format_c_14_credit_indicator(c_14_credit_indicator_test_df), rownames=FALSE)
```

c_14_credit_indicator_real_df for the real data
```{r}
DT::datatable(format_c_14_credit_indicator(c_14_credit_indicator_real_df), rownames=FALSE)
```

