---
title: "C-17"
author: "Craig Demke"
date: '2022-06-14'
output: html_document
---
```{r set global chunks, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE
)
```

```{r load libraries}
library(tidyverse)
library(datasets)
library(plotly)
library(gt)
library(glue)
library(stringr)
library(DT)
library(purrr)
```
## This is part of the Course Data Submission to USHE Element C-17
ELEMENT NAME: Section Days 1 
FIELD NAME: C_DAYS 
FIELD FORMAT: Varchar, 7 Characters 
With one position for each day of week, starting with Monday. 

## This data is found in Edify from export.section_schedule table
```{}
SELECT course_reference_number,
       is_meets_monday,
       is_meets_tuesday,
       is_meets_wednesday,
       is_meets_thursday,
       is_meets_friday,
       is_meets_saturday,
       is_meets_sunday
FROM section_schedule;
```


### Create fake data that matches this.

```{r}
meets_test_df <- tibble(
  course_reference_number = sample(1:99999, 10),
  is_meets_monday = sample(c(TRUE, FALSE), 10, replace = TRUE),
  is_meets_tuesday = sample(c(TRUE, FALSE), 10, replace = TRUE),
  is_meets_wednesday = sample(c(TRUE, FALSE), 10, replace = TRUE),
  is_meets_thursday = sample(c(TRUE, FALSE), 10, replace = TRUE),
  is_meets_friday = sample(c(TRUE, FALSE), 10, replace = TRUE),
  is_meets_saturday = sample(c(TRUE, FALSE), 10, replace = TRUE),
  is_meets_sunday = sample(c(TRUE, FALSE), 10, replace = TRUE)
) 

DT::datatable(meets_test_df)
```

### Now let's see if we can pull in real data

```{r}
### We pull the data we want from Edify
library(here)
source(here::here("R", "data_io_util.R"))

real_c17_df <- get_data_from_sql_file(file_name="c_17.sql",
                             dsn="edify")
# display data pulled in table
DT::datatable(real_c17_df, rownames=FALSE)
```

## ## Here is the R script

The first thing I need to do is to figure out how to turn a true into a letter and false into a space. We use a case_when statement to changes the boolean logic of true or false into the USHE race field value. example: If is_meets_monday is coded as TRUE then there will be a new variable called "M" in the column called M

```{r}
# TODO: talk with Andrea about what to do with missing values.
  # TODO: What to do if the input is not a boolean value.


change_meet <- real_c17_df %>%
  mutate(M = case_when(
    is_meets_monday == TRUE ~ "M",
    is_meets_monday == FALSE ~ "",
    TRUE ~ "mistake")) %>% 
  mutate(T = case_when(
    is_meets_tuesday == TRUE ~ "T",
    is_meets_tuesday == FALSE ~ "",
    TRUE ~ "mistake")) %>%
  mutate(W = case_when(
    is_meets_wednesday ==  TRUE ~ "W",
    is_meets_wednesday == FALSE ~ "",
    TRUE ~ "mistake")) %>%
  mutate(R = case_when(
    is_meets_thursday == TRUE ~ "R",
    is_meets_thursday == FALSE ~ "",
    TRUE ~ "mistake")) %>%
  mutate(F = case_when(
    is_meets_friday == TRUE ~ "F",
    is_meets_friday == FALSE ~ "",
    TRUE ~ "mistake")) %>%
  mutate(S = case_when(
    is_meets_saturday == TRUE ~ "S",
    is_meets_saturday == FALSE ~ "",
    TRUE ~ "mistake")) %>%
  mutate(U = case_when(
    is_meets_sunday == TRUE ~ "U",
    is_meets_sunday == FALSE ~ "",
    TRUE ~ "mistake"))

change_meet$"C-17" = paste(change_meet$M, change_meet$T, change_meet$W, change_meet$R, change_meet$F, change_meet$S, change_meet$U)


DT::datatable(change_meet)



```

Here we want to only run the crn numbers and USHE data. 
```{r}
only_crn_and_ushe_data <- change_meet %>% 
  select(course_reference_number, "C-17")

DT::datatable(only_crn_and_ushe_data)


```

Making the function for days of the week C-17

```{r}
format_c_17 <- function(input_df) {
  
  output_df <- input_df %>%
     mutate(M = case_when(
    is_meets_monday == TRUE ~ "M",
    is_meets_monday == FALSE ~ "",
    TRUE ~ "mistake")) %>% 
  mutate(T = case_when(
    is_meets_tuesday == TRUE ~ "T",
    is_meets_tuesday == FALSE ~ "",
    TRUE ~ "mistake")) %>%
  mutate(W = case_when(
    is_meets_wednesday ==  TRUE ~ "W",
    is_meets_wednesday == FALSE ~ "",
    TRUE ~ "mistake")) %>%
  mutate(R = case_when(
    is_meets_thursday == TRUE ~ "R",
    is_meets_thursday == FALSE ~ "",
    TRUE ~ "mistake")) %>%
  mutate(F = case_when(
    is_meets_friday == TRUE ~ "F",
    is_meets_friday == FALSE ~ "",
    TRUE ~ "mistake")) %>%
  mutate(S = case_when(
    is_meets_saturday == TRUE ~ "S",
    is_meets_saturday == FALSE ~ "",
    TRUE ~ "mistake")) %>%
  mutate(U = case_when(
    is_meets_sunday == TRUE ~ "U",
    is_meets_sunday == FALSE ~ "",
    TRUE ~ "mistake"))

output_df$"C-17" = paste(output_df$M, output_df$T, output_df$W,
                           output_df$R, output_df$F, output_df$S,
                           output_df$U)



return(output_df)
}
    
```

## Choose which data frame you want pass through the function 

meets_test_df for the fake data set
```{r}
DT::datatable(format_c_17(meets_test_df))
```

real_c17_df for the real data
```{r}
DT::datatable(format_c_17(real_c17_df))
```

