---
title: "c_44_instruct_type"
author: "Craig Demke"
date: '2022-06-17'
output: html_document
---

---
title: "instruct_type"
output: html_document
date: '2022-06-01'
---

```{r set global chunks, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE
)
```

```{r load libraries}
library(tidyverse)
library(datasets)
library(plotly)
library(gt)
library(glue)
library(stringr)
library(DT)
library(purrr)
library(here)
```
## This is part of the course data 
Element: C-44 
ELEMENT NAME: Instructional Type 
FIELD NAME: C_INSTRUCT_TYPE 
FIELD FORMAT: Varchar, 3 Characters 

## This data is found in Edify int the student_section table with the section_format_type_code column
```{}
SELECT DISTINCT (section_format_type_desc),
       section_format_type_code
FROM student_section;
```


### Create fake data that matches this.

```{r}
instruct_type_test_df <- tibble(
  course_reference_number = sample(1:99999, 10),
  section_format_type_code = sample(c("LEV", "MUN", "INV", "LBV", "LEX", "PRA", "LAB", "LBS", "STU", "LES", "
                       SUP", "LEC", "ENS", "INT", "THE", "CLS", "LEL", "LBC", "INS", "
                       CLN", "OTH", "MUM", "ACT", "CON"), 10, replace = TRUE))

   

DT::datatable(instruct_type_test_df, rownames=FALSE)
```

### Now let's see if we can pull in real data

```{r}
### We pull the data we want from the report database REPT 
library(here)
source(here::here("R", "data_io_util.R"))

instruct_type_real_df <- get_data_from_sql_file(file_name="c_44.sql",
                             dsn="edify")
# display data pulled in table
DT::datatable(instruct_type_real_df, rownames=FALSE)
```


## Here is the R script

The first thing I need to do is change each edify data point to the USHE data point

```{r}

change_instruct_type_df <- instruct_type_test_df %>%  
  mutate(instruct_type = case_when(
    section_format_type_code ==	"LEV"	~	"LEC", #TODO is this right
    section_format_type_code ==	"LEX"	~	"LEC",
    section_format_type_code ==	"LES"	~	"LEC", #TODO is this right
    section_format_type_code ==	"LEC"	~	"LEC",
    section_format_type_code ==	"INS"	~	"LEC",
    section_format_type_code ==	"STU"	~	"LEL",
    section_format_type_code ==	"ENS"	~	"LEL",
    section_format_type_code ==	"LEL"	~	"LEL",
    section_format_type_code ==	"LBV"	~	"LAB", #TODO is this right
    section_format_type_code ==	"LAB"	~	"LAB",
    section_format_type_code ==	"LBS"	~	"LAB", #TODO is this right
    section_format_type_code ==	"LBC"	~	"LAB",
    section_format_type_code ==	"PRA"	~	"SUP",
    section_format_type_code ==	"SUP"	~	"SUP",
    section_format_type_code ==	"INT"	~	"SUP",
    section_format_type_code ==	"CLN"	~	"SUP",
    section_format_type_code ==	"MUN"	~	"INV",
    section_format_type_code ==	"INV"	~	"INV",
    section_format_type_code ==	"MUN" ~	"INV",
    section_format_type_code ==	"ACT"	~	"INV",
    section_format_type_code ==	"THE"	~	"THE",
    section_format_type_code ==	"CON"	~	"CON", #TODO is this right according to USHE pdf
    section_format_type_code ==	"CLS"	~	"OTH",
    section_format_type_code ==	"OTH"	~	"OTH",
    TRUE ~ "error"))



DT::datatable(change_instruct_type_df)



```

## Making a function

```{r}

format_instruct_type <- function(input_df) {
  
  output_df <- input_df %>%  
  mutate(instruct_type = case_when(
    section_format_type_code ==	"LEV"	~	"LEC", #TODO is this right
    section_format_type_code ==	"LEX"	~	"LEC",
    section_format_type_code ==	"LES"	~	"LEC", #TODO is this right
    section_format_type_code ==	"LEC"	~	"LEC",
    section_format_type_code ==	"INS"	~	"LEC",
    section_format_type_code ==	"STU"	~	"LEL",
    section_format_type_code ==	"ENS"	~	"LEL",
    section_format_type_code ==	"LEL"	~	"LEL",
    section_format_type_code ==	"LBV"	~	"LAB", #TODO is this right
    section_format_type_code ==	"LAB"	~	"LAB",
    section_format_type_code ==	"LBS"	~	"LAB", #TODO is this right
    section_format_type_code ==	"LBC"	~	"LAB",
    section_format_type_code ==	"PRA"	~	"SUP",
    section_format_type_code ==	"SUP"	~	"SUP",
    section_format_type_code ==	"INT"	~	"SUP",
    section_format_type_code ==	"CLN"	~	"SUP",
    section_format_type_code ==	"MUN"	~	"INV",
    section_format_type_code ==	"INV"	~	"INV",
    section_format_type_code ==	"MUN" ~	"INV",
    section_format_type_code ==	"ACT"	~	"INV",
    section_format_type_code ==	"THE"	~	"THE",
    section_format_type_code ==	"CON"	~	"CON", #TODO is this right according to USHE pdf
    section_format_type_code ==	"CLS"	~	"OTH",
    section_format_type_code ==	"OTH"	~	"OTH",
    TRUE ~ "error"))
  
  
  return(output_df)
  
}
```
## Choose which data frame you want pass through the function 

instruct_type_test_df for the fake data set
```{r}
DT::datatable(format_instruct_type(instruct_type_test_df))
```

instruct_type_real_df for the real data
```{r}
DT::datatable(format_instruct_type(instruct_type_real_df))
```

