---
title: "C_50_delievery_model"
author: "Craig Demke"
date: '2022-06-22'
output: html_document
---

```{r set global chunks, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE
)
```

```{r load libraries}
library(tidyverse)
library(datasets)
library(plotly)
library(gt)
library(glue)
library(stringr)
library(DT)
library(purrr)
library(here)
```
## This is part of the Course Data
ELEMENT NAME: Delivery Model 
FIELD NAME: C_ DELIVERY_MODEL 
FIELD FORMAT: Varchar, 1 Character 
DEFINITION: The model in which the course was taught. 

This data is found in Edify from export.student_section, instruction_method_code.
```{}
SELECT DISTINCT (instruction_method_code)
FROM student_section;
```


### Create fake data that matches this.

```{r}
c_50_delivery_model_test_df <- tibble(
  course_reference_number = sample(1:99999, 10),
  instruction_method_code = sample(c("B", "V", " ", "E", "R", "I", "P", "H", "O", "T", NULL), 10, replace = TRUE))

DT::datatable(c_50_delivery_model_test_df, rownames=FALSE)
```

### Now let's see if we can pull in real data

```{r}
### We pull the data we want from the report database REPT 
library(here)
source(here::here("R", "data_io_util.R"))

c_50_delivery_model_real_df <- get_data_from_sql_file(file_name="c_50.sql",
                             dsn="edify")
# display data pulled in table
DT::datatable(c_50_delivery_model_real_df, rownames=FALSE)
```


## Here is the R script

The first thing I need to do is to figure out how to

```{r}

change_c_50_delivery_model_df <- c_50_delivery_model_test_df %>%
   mutate(c_50_delivery_model = case_when(
    instruction_method_code == "B" ~ 'B',
    instruction_method_code == "V" ~ '?', # need to check
    instruction_method_code == " " ~ "P", # need to check
    instruction_method_code == "E" ~ 'H', # need to check
    instruction_method_code == "R" ~ '?', # need to check
    instruction_method_code == "I" ~ '?', # need to check
    instruction_method_code == "P" ~ '?', # need to check
    instruction_method_code == "H" ~ '?', # need to check
    instruction_method_code == "O" ~ 'O',
    instruction_method_code == "T" ~ 'T',
    TRUE ~ instruction_method_code))


DT::datatable(change_c_50_delivery_model_df, rownames=FALSE)



```

## Making a function

```{r}

format_c_50_delivery_model <- function(input_df) {
  
  output_df <- input_df %>% 
  mutate(delivery_model = case_when(
    instruction_method_code == "B" ~ 'B',
    instruction_method_code == "V" ~ '?', # need to check
    instruction_method_code == " " ~ "P", # need to check
    instruction_method_code == "E" ~ 'H', # need to check
    instruction_method_code == "R" ~ '?', # need to check
    instruction_method_code == "I" ~ '?', # need to check
    instruction_method_code == "P" ~ '?', # need to check
    instruction_method_code == "H" ~ '?', # need to check
    instruction_method_code == "O" ~ 'O',
    instruction_method_code == "T" ~ 'T',
    TRUE ~ instruction_method_code))
 
  
  output_df <- output_df %>% 
  #select(delivery_model)
  
  return(output_df)
  
}
```
## Choose which data frame you want pass through the function 

c_50_delivery_model_test_df for the fake data set
```{r}
DT::datatable(format_c_50_delivery_model(c_50_delivery_model_test_df), rownames=FALSE)
```

c_50_delivery_model_real_df for the real data
```{r}
DT::datatable(format_c_50_delivery_model(c_50_delivery_model_real_df), rownames=FALSE)
```
