---
title: "C-51_course_level"
author: "Craig Demke"
date: '2022-06-22'
output: html_document
---

title: "c_51_course_level"
output: html_document
date: '2022-06-01'
---

```{r set global chunks, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE
)
```

```{r load libraries}
library(tidyverse)
library(datasets)
library(plotly)
library(gt)
library(glue)
library(stringr)
library(DT)
library(purrr)
library(here)
```
## This is part of the Course Data
ELEMENT NAME: Course Level 
FIELD NAME: C_ LEVEL 
FIELD FORMAT: Varchar, 1 Character 
DEFINITION: Indicates whether the course is offered as remedial or for undergraduate or  graduate level credit. 


## This data is found in Edify from Why are we not pulling in course_level_id?
```{}
SELECT DISTINCT (course_number),
                subject_code,
                course_level_id
FROM student_section;
```


### Create fake data that matches this.

```{r}
c_51_course_level_test_df <- tibble(
  course_number = sample(1:4999, 10),
  subject_code = sample(c("MATH", "ENGL", "ESL", "OTHER"), 10, replace = TRUE),
  course_level_id = sample(c("UG", "NC", "GR", "CE"), 10, replace = TRUE)
)

DT::datatable(c_51_course_level_test_df, rownames=FALSE)
```

### Now let's see if we can pull in real data

```{r}
### We pull the data we want from the report database REPT 
library(here)
source(here::here("R", "data_io_util.R"))

c_51_course_level_real_df <- get_data_from_sql_file(file_name="c_51.sql",
                             dsn="edify")
# display data pulled in table
DT::datatable(c_51_course_level_real_df, rownames=FALSE)
```


## Here is the R script

The first thing I need to do is to figure out how to find the remedial level courses there are 3 data points we need to have to get these. level id (UG), subject code (ENGL, MATH, ESL), and course number (< 1000)

```{r}

change_c_51_course_level_df <- c_51_course_level_test_df %>%
   mutate(course_level = case_when(
    course_level_id == "UG" & course_number <= 1000 &
      (subject_code == "ENGL" | subject_code == "ESL" | subject_code == "MATH")  ~ 'R',
    course_level_id == "UG" ~ 'U',
    course_level_id == "GR" ~ 'G',
    course_level_id == "NC" ~ 'U',
    course_level_id == "CE" ~ 'U',# is this right?
      TRUE ~ "error"))
  


DT::datatable(change_c_51_course_level_df, rownames=FALSE)



```

## Making a function

```{r}

format_c_51_course_level <- function(input_df) {
  
  output_df <- input_df %>%
  mutate(course_level = case_when(   
    course_level_id == "UG" & course_number <= 1000 &
      (subject_code == "ENGL" | subject_code == "ESL" | subject_code == "MATH")  ~ 'R',
    course_level_id == "UG" ~ 'U',
    course_level_id == "GR" ~ 'G',
    course_level_id == "NC" ~ 'U',
    course_level_id == "CE" ~ 'U',
      TRUE ~ "error"))
 
  
  output_df <- output_df %>% 
  #select(course_level)
  
  return(output_df)
  
}
```
## Choose which data frame you want pass through the function 

c_51_course_level_test_df for the fake data set
```{r}
DT::datatable(format_c_51_course_level(c_51_course_level_test_df), rownames=FALSE)
```

c_51_course_level_real_df for the real data
```{r}
DT::datatable(format_c_51_course_level(c_51_course_level_real_df), rownames=FALSE)
```
