---
title: "G-08 Date of Graduation"
author: "Craig Demke"
date: '2022-06-27'
output: html_document
---

```{r set global chunks, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE
)
```

```{r load libraries}
library(tidyverse)
library(datasets)
library(plotly)
library(gt)
library(glue)
library(stringr)
library(DT)
library(purrr)
library(here)
library(lubridate)
```
### This is part of the Graduatation Data Element: G-08
* ELEMENT NAME: Date of Graduation 
* FIELD NAME: G_DATE 
* FIELD FORMAT: Varchar, 8 Characters (YYYYMMDD Format) 
* DEFINITION: The calendar date the formal award was conferred by the institution. 

### This data is found in Edify from export.student, graduation_date
```{}
SELECT graduation_date
FROM export.degrees_awarded;
```


### Create fake data that matches this. we need to make some fake data that is in this format yyyy-mm-dd

```{r}
g_08_date_of_graduation_test_df <- tibble(
  graduation_date_year = sample(1978:2010, 10, replace = TRUE),
  graduation_date_month = sample(01:12, 10, replace = TRUE),
  graduation_date_day = sample(01:29, 10, replace = TRUE)) %>% 
  mutate(graduation_date_month = str_pad(graduation_date_month, 2, pad = '0')) %>% 
  mutate(graduation_date_day = str_pad(graduation_date_day, 2, pad = '0'))
  
 g_08_date_of_graduation_test_df$"graduation_date" =
   paste(g_08_date_of_graduation_test_df$graduation_date_year, 
         g_08_date_of_graduation_test_df$graduation_date_month, 
         g_08_date_of_graduation_test_df$graduation_date_day, sep = "-")
 
 g_08_date_of_graduation_test_df <- g_08_date_of_graduation_test_df %>%
  mutate(graduation_date = as_date(graduation_date)) %>% 
   select(graduation_date)
 

   

DT::datatable(g_08_date_of_graduation_test_df, rownames=FALSE)
```

### Now let's see if we can pull in real data

```{r}
### We pull the data we want from the report database REPT 
library(here)
source(here::here("R", "data_io_util.R"))

g_08_date_of_graduation_real_df <- get_data_from_sql_file(file_name="g_08.sql",
                             dsn="edify")
# display data pulled in table
DT::datatable(g_08_date_of_graduation_real_df, rownames=FALSE)
```


### Here is the R script

The first thing I need to do is to figure out how to remove the dashes in the date format. We need to convert yyyy-mm-dd to yyyymmdd. We can do this by using a gsub function.

```{r}

change_g_08_date_of_graduation_df <- g_08_date_of_graduation_test_df
 
  change_g_08_date_of_graduation_df$graduation_date <- gsub("-", "", change_g_08_date_of_graduation_df$graduation_date)
    
  


DT::datatable(change_g_08_date_of_graduation_df, rownames=FALSE)



```

### Making a function that will pass any data frame with the date of birth varable in the original format

```{r}

format_g_08_date_of_graduation <- function(input_df) {
  
  output_df <- input_df 
 
    output_df$graduation_date <- gsub("-", "", output_df$graduation_date) 
  
  
  return(output_df)
  
}
```
## Choose which data frame you want pass through the function 

g_08_date_of_graduation_test_df for the fake data set
```{r}
DT::datatable(format_g_08_date_of_graduation(g_08_date_of_graduation_test_df), rownames=FALSE)
```

g_08_date_of_graduation_real_df for the real data
```{r}
DT::datatable(format_g_08_date_of_graduation(g_08_date_of_graduation_real_df), rownames=FALSE)
```
