---
title: "PF-05 Degree TYPE"
author: "Craig Demke"
date: "`r Sys.Date()`"
output: html_document
---
```{r set global chunks, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE
)
```

```{r load libraries}
library(tidyverse)
library(datasets)
library(plotly)
library(gt)
library(glue)
library(stringr)
library(DT)
library(purrr)
library(here)
```


### This is part of the Programs File Element: P-05 
*   ELEMENT NAME: Degree Type
	
*   FIELD NAME: PF_DEG_TYPE

*   FIELD FORMAT: Varchar, 13 Characters

* DEFINITION: 
The acronym which refers to the type of degree being award. For all certificates, master’s and doctor’s degrees, institutions may submit the acronyms currently in use by their institution. 
For associate’s and bachelor’s degrees, institutions must choose the value from the table below that best represents institution awards at the same IPEDS degree level and CIP code. 



### This data is found in Edify from export.academic_programs degree_id 
```{}
SELECT degree_id
FROM export.academic_programs
WHERE degree_id = 'MMFT
LIMIT 10;
```


### Create fake data that matches the degree type in Edify

```{r}
pf_05_degree_type_test_df <- tibble(
  degree_id = sample(c("AS","MMFT", "BS"), 23, replace = TRUE)
 
)
   

DT::datatable(pf_05_degree_type_test_df, rownames=FALSE)
```

### Now let's see if we can pull in real data

```{r}
### We pull the data we want from the report database REPT 
pf_05_degree_type_real_df <- utHelpR::get_data_from_sql_file(file_name="pf_05.sql",
                                               dsn="edify",
                                               context="sandbox")
# display data pulled in table
DT::datatable(pf_05_degree_type_real_df, rownames=FALSE)
```


### Here is the R script

The first thing I need to do is to figure out how to filter out any degrees which have not been awarded

```{r}

change_pf_05_degree_type_df <- pf_05_degree_type_test_df %>%
  mutate(degree_type = ifelse(degree_id == "MMFT", "MMF", degree_id ))

DT::datatable(change_pf_05_degree_type_df, rownames=FALSE)

```

### Making a function

```{r}

format_pf_05_degree_type <- function(input_df, with_intermediates=FALSE) {
  
  output_df <- input_df %>%  
    mutate(pf_degree_type = ifelse(degree_id == "MMFT", "MMF", degree_id )) %>% 
    mutate(pf_05 = (pf_degree_type)) 
  
    if (!with_intermediates) {
      output_df <- output_df %>%
        select(-c(pf_degree_type))
    }

  return(output_df)
  
}

```


### Choose which data frame you want pass through the function 

pf_05_degree_type_test_df for the fake data set
```{r}
DT::datatable(format_pf_05_degree_type(pf_05_degree_type_test_df), rownames=FALSE)
```

pf_05_degree_type_real_df for the real data
```{r}
DT::datatable(format_pf_05_degree_type(pf_05_degree_type_real_df), rownames=FALSE)
```

