---
title: "S-14"
output: html_document
date: '2022-06-01'
---

```{r set global chunks, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE
)
```

```{r load libraries}
library(tidyverse)
library(datasets)
library(plotly)
library(gt)
library(glue)
library(stringr)
library(DT)
library(purrr)
library(here)
```
## This is part of the Student Data Submission to USHE Element S-14
ELEMENT NAME: Ethnic Origin 
FIELD NAME: S_ETHNIC 
FIELD FORMAT: Varchar, 8 Characters,  
DEFINITION: The racial and ethnic categories used to classify students.

## This data is found in Edify from export.student table
```{}
SELECT s.student_id,
       s.is_hispanic_latino_ethnicity,
       s.is_asian,
       s.is_black,
       s.is_american_indian_alaskan,
       s.is_hawaiian_pacific_islander,
       s.is_white,
       s.is_international,
       s.is_other_race
FROM export.student s;
```


### Create fake data that matches this.

```{r}
test_df <- tibble(
  student_id = sample(1:999999, 10),
  is_hispanic_latino_ethnicity = sample(c(TRUE, FALSE), 10, replace = TRUE),
  is_asian = sample(c(TRUE, FALSE), 10, replace = TRUE),
  is_black = sample(c(TRUE, FALSE), 10, replace = TRUE),
  is_american_indian_alaskan = sample(c(TRUE, FALSE), 10, replace = TRUE),
  is_hawaiian_pacific_islander = sample(c(TRUE, FALSE), 10, replace = TRUE),
  is_white = sample(c(TRUE, FALSE), 10, replace = TRUE),
  is_international = sample(c(TRUE, FALSE), 10, replace = TRUE),
  is_other_race = sample(c(TRUE, FALSE), 10, replace = TRUE)
) %>% 
    mutate(person_id = str_pad(student_id, 8, pad = '0'))

DT::datatable(test_df)
```

### Now let's see if we can pull in real data

```{r}
### We pull the data we want from the report database REPT 
library(here)
source(here::here("R", "data_io_util.R"))

real_df <- get_data_from_sql_file(file_name="s_14.sql",
                             dsn="edify")
# display data pulled in table
DT::datatable(real_df, rownames=FALSE)
```


## Here is the R script

The first thing I need to do is to figure out how to turn a true into a letter and false into a space. We use a case_when statement to changes the boolean logic of true or false into the USHE race field value. example: If is_hispanic_latino_ethnicity is coded as TRUE then there will be a new variable called "H" in the column called H

```{r}
# TODO: talk with Andrea about what to do with missing values.
  # TODO: What to do if the input is not a boolean value.

change_race <- test_df %>%  
  mutate(H = case_when(
    is_hispanic_latino_ethnicity == TRUE ~ "H",
    is_hispanic_latino_ethnicity == FALSE ~ " ",
    TRUE ~ " ")) %>% 
  mutate(A = case_when(
    is_asian == TRUE ~ "A",
    is_asian == FALSE ~ " ",
    TRUE ~ " ")) %>%
  mutate(B = case_when(
    is_black ==  TRUE ~ "B",
    is_black == FALSE ~ " ",
    TRUE ~ " ")) %>%
  mutate(I = case_when(
    is_american_indian_alaskan == TRUE ~ "I",
    is_american_indian_alaskan == FALSE ~ " ",
    TRUE ~ " ")) %>%
  mutate(P = case_when(
    is_hawaiian_pacific_islander == TRUE ~ "P",
    is_hawaiian_pacific_islander == FALSE ~ " ",
    TRUE ~ " ")) %>%
  mutate(W = case_when(
    is_white == TRUE ~ "W",
    is_white == FALSE ~ " ",
    TRUE ~ " ")) %>%
  mutate(N = case_when(
    is_international == TRUE ~ "N",
    is_international == FALSE ~ " ",
    TRUE ~ " ")) %>%
  mutate(U = case_when(
    is_other_race == TRUE ~ "U",
    is_other_race == FALSE ~ " ",
    TRUE ~ " ")) # here I took out "mistake" and just put in a space because it was NA

change_race$"S-14" = paste(change_race$H, change_race$A, change_race$B,
                           change_race$I,change_race$P, change_race$W,
                           change_race$N, change_race$U)

change_race$"S-14" <- gsub('\\s  ', '', change_race$"S-14")


DT::datatable(change_race)



```

Here we want to only run the d-numbers and ushe data. This data should have all of the spaces included in the raw table only_numbers_and_ushe_data
```{r}
only_numbers_and_ushe_data <- change_race %>% 
  select(student_id, "S-14")

DT::datatable(only_numbers_and_ushe_data)


```

## Making a function

```{r}

format_s_14 <- function(input_df) {
  
  output_df <- input_df %>%  
  mutate(H = case_when(
    is_hispanic_latino_ethnicity == TRUE ~ "H",
    is_hispanic_latino_ethnicity == FALSE ~ "",
    TRUE ~ "mistake")) %>% 
  mutate(A = case_when(
    is_asian == TRUE ~ "A",
    is_asian == FALSE ~ "",
    TRUE ~ "mistake")) %>%
  mutate(B = case_when(
    is_black ==  TRUE ~ "B",
    is_black == FALSE ~ "",
    TRUE ~ "mistake")) %>%
  mutate(I = case_when(
    is_american_indian_alaskan == TRUE ~ "I",
    is_american_indian_alaskan == FALSE ~ "",
    TRUE ~ "mistake")) %>%
  mutate(P = case_when(
    is_hawaiian_pacific_islander == TRUE ~ "P",
    is_hawaiian_pacific_islander == FALSE ~ "",
    TRUE ~ "mistake")) %>%
  mutate(W = case_when(
    is_white == TRUE ~ "W",
    is_white == FALSE ~ "",
    TRUE ~ "mistake")) %>%
  mutate(N = case_when(
    is_international == TRUE ~ "N",
    is_international == FALSE ~ "",
    TRUE ~ "mistake")) %>%
  mutate(U = case_when(
    is_other_race == TRUE ~ "U",
    is_other_race == FALSE ~ "",
    TRUE ~ "")) # here I took out "mistake" and just put in a space because it was NA
  
  output_df$"S-14" = paste(output_df$H, output_df$A, output_df$B, 
                           output_df$I, output_df$P, output_df$W, 
                           output_df$N, output_df$U)
  
  output_df <- output_df %>% 
  select(student_id, "S-14")
  
  return(output_df)
  
}
```
## Choose which data frame you want pass through the function 

meets_test_df for the fake data set
```{r}
DT::datatable(format_s_14(test_df))
```

real_c17_df for the real data
```{r}
DT::datatable(format_s_14(real_df))
```

