---
title: "S-15 Regent Residency Status"
author: "Craig Demke"
date: '2022-06-23'
output: html_document
---


```{r set global chunks, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE
)
```

```{r load libraries}
library(tidyverse)
library(datasets)
library(plotly)
library(gt)
library(glue)
library(stringr)
library(DT)
library(purrr)
library(here)
```
### This is part of the Students Data Element: S-15 
* ELEMENT NAME: Regent Residency Status 
* FIELD NAME: S_REGENT_RES 
* FIELD FORMAT: Varchar, 1 Character, 

### This data is found in Edify from export.student_term_level, residency code
```{}
SELECT residency_code
FROM student_term_level;
```


### Create fake data that matches this.

```{r}
s_15_regent_residency_status_test_df <- tibble(
 residency_code = sample(c("S", "R", "A", "N", "C", "0", "H", "M", "G"), 10, replace = TRUE)) 
# this is a zero and not the letter O

   

DT::datatable(s_15_regent_residency_status_test_df, rownames=FALSE)
```

### Now let's see if we can pull in real data

```{r}
### We pull the data we want from the report database REPT 
library(here)
source(here::here("R", "data_io_util.R"))

s_15_regent_residency_status_real_df <- get_data_from_sql_file(file_name="s_15.sql",
                             dsn="edify")

# display data pulled in table
DT::datatable(s_15_regent_residency_status_real_df, rownames=FALSE)
```


### Here is the R script

The first thing we do is convert the Utah Tech residency code to the USHE s_regent_res code.

```{r}

change_s_15_regent_residency_status_df <- s_15_regent_residency_status_test_df %>%
   mutate( s_regent_res = case_when(
     residency_code == "R" ~ 'R',
     residency_code == "C" ~ 'R',
     residency_code == "N" ~ 'N',
     residency_code == "S" ~ ' ',
     residency_code == "H" ~ 'N',
     residency_code == "0" ~ ' ', # this is a zero and not the letter O
     residency_code == "A" ~ 'A',
     residency_code == "M" ~ 'M',
     residency_code == "G" ~ 'G',
     TRUE ~ "error"))
  


DT::datatable(change_s_15_regent_residency_status_df, rownames=FALSE)



```

### Making a function  


```{r}

format_s_15_regent_residency_status <- function(input_df) {
  
  output_df <- input_df %>%  
     mutate( s_regent_res = case_when(
     residency_code == "R" ~ 'R',
     residency_code == "C" ~ 'R',
     residency_code == "N" ~ 'N',
     residency_code == "S" ~ ' ',
     residency_code == "H" ~ 'N',
     residency_code == "0" ~ ' ', # this is a zero and not the letter O
     residency_code == "A" ~ 'A',
     residency_code == "M" ~ 'M',
     residency_code == "G" ~ 'G',
     TRUE ~ "error"))

  return(output_df)
  
}
```
### Choose which data frame you want pass through the function 

s_15_regent_residency_status_test_df for the fake data set
```{r}
DT::datatable(format_s_15_regent_residency_status(s_15_regent_residency_status_test_df), rownames=FALSE)
```

s_15_regent_residency_status_real_df for the real data
```{r}
DT::datatable(format_s_15_regent_residency_status(s_15_regent_residency_status_real_df), rownames=FALSE)
```
