---
title: "S-17 Registration Status"
author: "Craig Demke"
date: '2022-06-23'
output: html_document
---

```{r set global chunks, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE
)
```

```{r load libraries}
library(tidyverse)
library(datasets)
library(plotly)
library(gt)
library(glue)
library(stringr)
library(DT)
library(purrr)
library(here)
```
### This is part of the Students Data Element: S-17
* ELEMENT NAME: Registration Status 
* FIELD NAME: S_REG_STATUS 
* FIELD FORMAT: Varchar, 2 Characters,  
* DEFINITION: Student's entry status at the beginning of the term.

### This data is found in Edify from expoert.student_term_level, student_type_code
```{}
--S-17
SELECT student_type_code
FROM student_term_level;
```


### Create fake data that matches this.

```{r}
s_17_registration_status_test_df <- tibble(
  student_type_code = sample(c("3", "S", "2", "R", "5", "N", "C", "0", "P", "H", "1", "F", "T"), 13, replace = FALSE)
  ) 

DT::datatable(s_17_registration_status_test_df, rownames=FALSE)
```

### Now let's see if we can pull in real data

```{r}
### We pull the data we want from the report database REPT 
library(here)
source(here::here("R", "data_io_util.R"))

s_17_registration_status_real_df <- get_data_from_sql_file(file_name="s_17.sql",
                             dsn="edify")
# display data pulled in table
DT::datatable(s_17_registration_status_real_df, rownames=FALSE)
```


### Here is the R script

The first thing I need to do is to figure out how to convert Utah Tech student_type_code to USHE s_reg_status

```{r}

change_s_17_registration_status_df <- s_17_registration_status_test_df %>%
   mutate(s_reg_status = case_when(
      student_type_code == "0" ~ '?', # Undeclared
      student_type_code == "1" ~ 'NG', # New Graduate
      student_type_code == "2" ~ 'TG', # Transfer Graduate
      student_type_code == "3" ~ 'RG', # Readmit Graduate
      student_type_code == "5" ~ 'CG', # Continuing Graduate
      student_type_code == "C" ~ 'CS', # Continuing Registration
      student_type_code == "F" ~ 'FF', # Freshman
      student_type_code == "H" ~ 'HS', # High School
      student_type_code == "N" ~ 'FH', # New Freshman from HS
      student_type_code == "P" ~ 'CE', # Personal Interest, Non-Degree
      student_type_code == "R" ~ 'RS', # Readmit
      student_type_code == "S" ~ 'NC?', # Special
      student_type_code == "T" ~ 'TU', # Transfer
     TRUE ~ "error"))
  
DT::datatable(change_s_17_registration_status_df, rownames=FALSE)



```

### Making a function

```{r}

format_s_17_registration_status <- function(input_df) {
  
  output_df <- input_df %>%  
    mutate(s_reg_status = case_when(
      student_type_code == "0" ~ '?', # Undeclared
      student_type_code == "1" ~ 'NG', # New Graduate
      student_type_code == "2" ~ 'TG', # Transfer Graduate
      student_type_code == "3" ~ 'RG', # Readmit Graduate
      student_type_code == "5" ~ 'CG', # Continuing Graduate
      student_type_code == "C" ~ 'CS', # Continuing Registration
      student_type_code == "F" ~ 'FF', # Freshman
      student_type_code == "H" ~ 'HS', # High School
      student_type_code == "N" ~ 'FH', # New Freshman from HS
      student_type_code == "P" ~ 'CE', # Personal Interest, Non-Degree
      student_type_code == "R" ~ 'RS', # Readmit
      student_type_code == "S" ~ 'NC?', # Special
      student_type_code == "T" ~ 'TU', # Transfer
     TRUE ~ "error"))
  
  #output_df <- output_df %>% 
  #select(s_reg_status)
  
  return(output_df)
  
}
```
### Choose which data frame you want pass through the function 

s_17_registration_status_test_df for the fake data set
```{r}
DT::datatable(format_s_17_registration_status(s_17_registration_status_test_df), rownames=FALSE)
```

s_17_registration_status_real_df for the real data
```{r}
DT::datatable(format_s_17_registration_status(s_17_registration_status_real_df), rownames=FALSE)
```
