---
title: "S-20 Cumulative Institutional Undergraduate Hours"
author: "Craig Demke"
date: '2022-06-23'
output: html_document
---


```{r set global chunks, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE
)
```

```{r load libraries}
library(tidyverse)
library(datasets)
library(plotly)
library(gt)
library(glue)
library(stringr)
library(DT)
library(purrr)
library(here)
```
### This is part of the Student DataElement: S-20
* ELEMENT NAME: Cumulative Institutional Undergraduate Hours 
* FIELD NAME: S_CUM_HRS_UGRAD 
* FIELD FORMAT: Numeric(5,1) 
* DEFINITION: Total number of credit hours the student has earned as an undergraduate student at this  institution. Hours should be semester hours. Value should be zero for graduate students (see element S 18). (Does not include transfer hours.) 

### This data is found in Edify from export.student_term_level, institutional_cumulative_credits_earned, level_id
```{}
SELECT institutional_cumulative_credits_earned,
       level_id
FROM student_term_level;
```


### Create fake data that matches this.

```{r}
s_20_institutional_undergraduate_hours_test_df <- tibble(
  institutional_cumulative_credits_earned = sample(1:150, 10),
  level_id = sample(c("UG", "NC", "GR", "CE", "00", ""), 10, replace = TRUE)
) 
   

DT::datatable(s_20_institutional_undergraduate_hours_test_df, rownames=FALSE)
```

### Now let's see if we can pull in real data

```{r}
### We pull the data we want from the report database REPT 
library(here)
source(here::here("R", "data_io_util.R"))

s_20_institutional_undergraduate_hours_real_df <- get_data_from_sql_file(file_name="S_20.sql",
                             dsn="edify")
# display data pulled in table
DT::datatable(s_20_institutional_undergraduate_hours_real_df, rownames=FALSE)
```


### Here is the R script

The first thing I need to do is to figure out how to

```{r}

change_s_20_institutional_undergraduate_hours_df <- s_20_institutional_undergraduate_hours_test_df %>%
   mutate(institutional_undergraduate_hours = ifelse(level_id == "GR", 0, round(institutional_cumulative_credits_earned, digits = 1)))
            
DT::datatable(change_s_20_institutional_undergraduate_hours_df, rownames=FALSE)

```

### Making a function

```{r}

format_s_20_institutional_undergraduate_hours <- function(input_df) {
  
  output_df <- input_df %>%  
  mutate(institutional_undergraduate_hours = ifelse(level_id == "GR", 0, round(institutional_cumulative_credits_earned, digits = 1)))
                                                    
  
  output_df <- output_df %>% 
  select(institutional_undergraduate_hours)
  
  return(output_df)
  
}
```
### Choose which data frame you want pass through the function 

s_20_institutional_undergraduate_hours_test_df for the fake data set
```{r}
DT::datatable(format_s_20_institutional_undergraduate_hours(s_20_institutional_undergraduate_hours_test_df), rownames=FALSE)
```

s_20_institutional_undergraduate_hours_real_df for the real data
```{r}
DT::datatable(format_s_20_institutional_undergraduate_hours(s_20_institutional_undergraduate_hours_real_df), rownames=FALSE)
```

