---
title: "S-21 Cumulative Institutional Undergraduate GPA"
author: "Craig Demke"
date: '2022-06-24'
output: html_document
---

```{r set global chunks, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE
)
```

```{r load libraries}
library(tidyverse)
library(datasets)
library(plotly)
library(gt)
library(glue)
library(stringr)
library(DT)
library(purrr)
library(here)
```
### This is part of the Students Data Element: S-21 
* ELEMENT NAME: Cumulative Institutional Undergraduate GPA 
* FIELD NAME: S_CUM_GPA_UGRAD 
* FIELD FORMAT: Numeric (4,3) 
* DEFINITION: Student's Cumulative GPA as of the present academic term as an undergraduate  student. This should tie to Cumulative Institutional Hours field. No transfer hours are to be included.  All credit hours should represent average course grade on a 4.0 scale. This GPA ties to earned credits in  Cumulative Institutional Undergraduate Hours. Value should be zero for graduate students (see element  S-18). 


### This data is found in Edify from export.student_term_level, institutional_cumulative_gpa, level_id
```{}
SELECT institutional_cumulative_gpa,
       level_id
FROM student_term_level;
```


### Create fake data that matches this.

```{r}
sc_21_cumulative_institutional_undergraduate_gpa_test_df <- tibble(
  institutional_cumulative_gpa = sample(0.0:4.0, 10, replace = TRUE),
  level_id = sample(c("UG", "NC", "GR", "CE", "00", ""), 10, replace = TRUE)
)
   
DT::datatable(sc_21_cumulative_institutional_undergraduate_gpa_test_df, rownames=FALSE)
```

### Now let's see if we can pull in real data

```{r}
### We pull the data we want from the report database REPT 
library(here)
source(here::here("R", "data_io_util.R"))

sc_21_cumulative_institutional_undergraduate_gpa_real_df <- get_data_from_sql_file(file_name="s_21.sql",
                             dsn="edify")
# display data pulled in table
DT::datatable(sc_21_cumulative_institutional_undergraduate_gpa_real_df, rownames=FALSE)
```


### Here is the R script

The first thing I need to do is to figure out how to

```{r}

change_sc_21_cumulative_institutional_undergraduate_gpa_df <- sc_21_cumulative_institutional_undergraduate_gpa_test_df %>%
   mutate(cumulative_institutional_undergraduate_gpa = ifelse(level_id == "GR", 0, round(institutional_cumulative_gpa, digits = 2)))
  
DT::datatable(change_sc_21_cumulative_institutional_undergraduate_gpa_df, rownames=FALSE)

```

### Making a function

```{r}

format_sc_21_cumulative_institutional_undergraduate_gpa <- function(input_df) {
  
  output_df <- input_df %>%
  mutate(cumulative_institutional_undergraduate_gpa = ifelse(level_id == "GR", 0, round(institutional_cumulative_gpa, digits = 2)))
  
  #output_df <- output_df %>% 
  #select(cumulative_institutional_undergraduate_gpa)
  
  return(output_df)
  
}
```
### Choose which data frame you want pass through the function 

sc_21_cumulative_institutional_undergraduate_gpa_test_df for the fake data set
```{r}
DT::datatable(format_sc_21_cumulative_institutional_undergraduate_gpa(sc_21_cumulative_institutional_undergraduate_gpa_test_df), rownames=FALSE)
```

sc_21_cumulative_institutional_undergraduate_gpa_real_df for the real data
```{r}
DT::datatable(format_sc_21_cumulative_institutional_undergraduate_gpa(sc_21_cumulative_institutional_undergraduate_gpa_real_df), rownames=FALSE)
```


