---
title: "Template"
author: "Craig Demke"
date: '2022-06-17'
output: html_document
---

---
title: "placeholder"
output: html_document
date: '2022-06-01'
---

```{r set global chunks, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE
)
```

```{r load libraries}
library(tidyverse)
library(datasets)
library(plotly)
library(gt)
library(glue)
library(stringr)
library(DT)
library(purrr)
library(here)
```
## This is part of the 


## This data is found in Edify from 
```{}

```


### Create fake data that matches this.

```{r}
placeholder_test_df <- tibble(
  
) %>% 
   

DT::datatable(placeholder_test_df, rownames=FALSE)
```

### Now let's see if we can pull in real data

```{r}
### We pull the data we want from the report database REPT 
library(here)
source(here::here("R", "data_io_util.R"))

real_df <- get_data_from_sql_file(file_name="placeholder.sql",
                             dsn="edify")
# display data pulled in table
DT::datatable(placeholder_real_df, rownames=FALSE)
```


## Here is the R script

The first thing I need to do is to figure out how to

```{r}

change_placeholder_df <- placeholder_test_df %>%
   mutate(placeholder = case_when(
  


DT::datatable(change_placeholder, rownames=FALSE)



```

## Making a function

```{r}

format_placeholder <- function(input_df) {
  
  output_df <- input_df %>%  
 
  
  output_df <- output_df %>% 
  select()
  
  return(output_df)
  
}
```
## Choose which data frame you want pass through the function 

placeholder_test_df for the fake data set
```{r}
DT::datatable(format_place_holder(placeholder_test_df), rownames=FALSE)
```

placeholder_real_df for the real data
```{r}
DT::datatable(format_place_holder(placeholder_real_df), rownames=FALSE)
```

