---
title: "C-02"
author: "Craig Demke"
date: '2022-06-15'
output: html_document
---

---
```{r set global chunks, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE
)
```

```{r load libraries}
library(tidyverse)
library(datasets)
library(plotly)
library(gt)
library(glue)
library(stringr)
library(DT)
library(purrr)
```
## This is part of the Course Data Submission to USHE Element C-02
ELEMENT NAME: Year, Term & Extract Code 
FIELD NAME: C_TERM_ID 
FIELD FORMAT: Number, 4 Characters (YYYY format) 
 Number, 1 Character (T format) 
 Varchar, 1 character (E format) 
DEFINITION: The current academic year, term, and extract in which course is offered. Format  YYYYTE is made up of academic year YYYY, academic term T, and extract E (3rd week or End of  Term). 

## This data is found in Edify from export.course_verson, and export.term
```{}
SELECT DISTINCT (s.course_id),
       t.academic_year_code,
       t.season,
       s.version_id
FROM export.student_section_version s
LEFT JOIN term t
    ON t.term_id = s.term_id
WHERE s.term_id = '202140'
LIMIT 10;
```


### Create fake data that matches this.

```{r}
year_term_extract_test_df <- tibble(
  academic_year_code = (2022),
  season = sample(c("Summer", "Fall", "Spring"), 10, replace = TRUE),
  version_id = sample(c(2, 3), 10, replace = TRUE)
) 

DT::datatable(year_term_extract_test_df, rownames=FALSE)
```

### Now let's see if we can pull in real data

```{r}
#We pull the data we want from Edify
library(here)
source(here::here("R", "data_io_util.R"))

real_c_02_df <- get_data_from_sql_file(file_name="c_02.sql",
                           dsn="edify")
 #display data pulled in table
DT::datatable(real_c_02_df, rownames=FALSE)
```

## Here is the R script

The first thing I need to do is to figure out how to
```{r}
# Adding conditional logic to determine c_term_id

change_year_term_extract <- year_term_extract_test_df %>%
  mutate(t_format = case_when(
    season == "Summer" ~ '1',
    season == "Fall" ~ '2',
    season == 'Spring' ~ '3',
    TRUE ~ "mistake")) %>% 
  mutate(v_format = case_when(
    version_id == '1' ~ 'current',
    version_id == '2' ~ '3',
    version_id == '3' ~ 'E',
    TRUE ~ "error"))

change_year_term_extract$"year_term_extract" = paste(change_year_term_extract$academic_year_code,
                                        change_year_term_extract$t_format,
                                        change_year_term_extract$v_format)

change_year_term_extract$Remove_all_space <- gsub('\\s+', '', change_year_term_extract$"year_term_extract")

DT::datatable(change_year_term_extract)

```

Now we write the function
```{r}
format_ushe_year_term_extract <- function(input_df) {
  
  output_df <- input_df %>%
    mutate(academic_year = str_sub(term_id, 1, 4)) %>% 
    mutate(last_year = (as.numeric(academic_year) - 1)) %>%
    mutate(season = str_sub(term_id, 5, 6)) %>%  
    mutate(academic_year_code = case_when(
      season == "30" ~ as.character(last_year),
      season == "40" ~ as.character(last_year),
      season == '20' ~ as.character(last_year),
      TRUE ~ "error")) %>% 
    mutate(t_format = case_when(
      season == "30" ~ '1',
      season == "40" ~ '2',
      season == '20' ~ '3',
      TRUE ~ "mistake")) %>% 
    mutate(v_format = case_when(
      version_id == '1' ~ 'current',
      version_id == '2' ~ '3',
      version_id == '3' ~ 'E',
      TRUE ~ "error"))

output_df$"year_term_extract" = paste(output_df$academic_year_code,
                                        output_df$t_format,
                                        output_df$v_format, sep = "")


output_df <- output_df %>%

return(output_df)

}
```
## Choose which data frame you want pass through the function 

 for the fake data set
```{r}
DT::datatable(format_ushe_year_term_extract(year_term_extract_test_df))
```

--- for the real data
```{r}
DT::datatable(format_ushe_year_term_extract(real_c_02_df))
```

