---
title: "C-08 Non-Credit Course Contact Hours"
author: "Craig Demke"
date: '2022-07-11'
output: html_document
---
```{r set global chunks, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE
)
```

```{r load libraries}
library(tidyverse)
library(datasets)
library(plotly)
library(gt)
library(glue)
library(stringr)
library(DT)
library(purrr)
library(here)
```
### This is part of the Course Data Element: C-08 
* ELEMENT NAME: Non-Credit Course Contact Hours 
* FIELD NAME: C_CONTACT_HRS 
* FIELD FORMAT: Numeric (5,0) 
* DEFINITION: The maximum number of contact hours the course is scheduled to meet within the  academic term. Sometimes referred to as clock hours. This field is for non-credit courses only. 


### This data is found in Edify from export.student_section_version, with course_level_id and contact_hours
```{}
SELECT DISTINCT (a.course_level_id),
       a.contact_hours
FROM student_section_version a;
```


### Create fake data that matches contact hours and course level id 

```{r}
c_08_nc_courses_contact_hours_test_df <- tibble(
  contact_hours = sample(c(1:9.0), 10, replace = TRUE),
  course_level_id = sample(c("CE", "UG", "GR", "NC"), 10, replace = TRUE)
)
   

DT::datatable(c_08_nc_courses_contact_hours_test_df, rownames=FALSE)
```

### Now let's see if we can pull in real data

```{r}
### We pull the data we want from the report database REPT 

c_08_nc_courses_contact_hours_real_df <- utHelpR::get_data_from_sql_file(file_name="c_08.sql",
                                               dsn="edify",
                                               context="sandbox")

# display data pulled in table
DT::datatable(c_08_nc_courses_contact_hours_real_df, rownames=FALSE)
```


### Here is the R script

The first thing I need to do is to figure out how to only display contact hours from non degree seeking courses

```{r}

change_c_08_nc_courses_contact_hours_df <- c_08_nc_courses_contact_hours_test_df %>%
    mutate( c_contact_hrs = ifelse(course_level_id == "CE" | course_level_id == "NC", contact_hours, "")) %>% 
    mutate( c_08 = course_level_id )
  
DT::datatable(change_c_08_nc_courses_contact_hours_df, rownames=FALSE)



```

### Making a function

```{r}
  
format_c_08_nc_courses_contact_hours <- function(input_df, with_intermediates=FALSE) {

  output_df <- input_df %>%
    mutate( c_contact_hrs = ifelse(course_level_id == "CE" | course_level_id == "NC", contact_hours, "")) %>% 
    mutate( c_08 = c_contact_hrs )

    if (!with_intermediates) {
      output_df <- output_df %>%
        select( -c(c_contact_hrs) )
    }

  return(output_df)

  
}
```
### Choose which data frame you want pass through the function 

c_08_nc_courses_contact_hours_test_df for the fake data set
```{r}
DT::datatable(format_c_08_nc_courses_contact_hours(c_08_nc_courses_contact_hours_test_df), rownames=FALSE)
```

c_08_nc_courses_contact_hours_real_df for the real data
```{r}
DT::datatable(format_c_08_nc_courses_contact_hours(c_08_nc_courses_contact_hours_real_df), rownames=FALSE)
```

