---
title: "C-10"
author: "Craig Demke"
date: '2022-06-16'
output: html_document
---

```{r set global chunks, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE
)
```

```{r load libraries}
library(tidyverse)
library(datasets)
library(plotly)
library(gt)
library(glue)
library(stringr)
library(DT)
library(purrr)
```
## This is part of the Course Data Submission to USHE Element C-10
ELEMENT NAME: Course Site Type 
FIELD NAME: C_SITE_TYPE 
FIELD FORMAT: Varchar, 3 Characters 
DEFINITION: Code used to specify a site type where instruction originates. 

## This data is found in Edify from export.student_section_version campus_id
```{}

```


### Create fake data that matches this.

```{r}
c_10_test_df <- tibble(
  course_reference_number = sample(1:99999, 10),
  campus_id = sample(c("A01", "AC1", "ACE", "AU1", "B80", "B8C", "C00", "C01", "C02", "C03", "C04",
                       "C05", "C06", "C07", "C08", "C09", "C10", "C11", "C12", "C13", "C14", "C15",
                       "C16", "C17", "C18", "C19", "C20", "C21", "C22", "C23", "C24", "C25", "C26",
                       "C27", "C28", "D07", "E04", "F10", "G", "H", "O01", "O02", "O03", "OCE", "OU1",
                       "UOS", "V01", "XXX", "Z"), 10, replace = TRUE))

DT::datatable(c_10_test_df, rownames=FALSE)
```

### Now let's see if we can pull in real data

```{r}
#We pull the data we want from Edify
library(here)
source(here::here("R", "data_io_util.R"))

real_c_10_df <- get_data_from_sql_file(file_name="c_10.sql",
                           dsn="edify")
 #display data pulled in table
DT::datatable(real_c_10_df, rownames=FALSE)
```

## Here is the R script

```{r}
# Adding conditional logic to determine c_term_id

changec_10_test_df <- c_10_test_df %>%
  mutate(site_type = case_when(
    campus_id == "AC1" ~ 'A01',
    campus_id == "AU1" ~ 'A01',
    campus_id == "ACE" ~ 'A01',
    campus_id == "B8C" ~ 'B80',
    campus_id == "UOS" ~ 'C',
    campus_id == "OU1" ~ 'O01', #TODO should this be A01
    campus_id == "V01" ~ 'O01', #TODO should this be A01
    str_sub(campus_id, 1, 1) == "C" ~ str_sub(campus_id, 1, 1),
    TRUE ~ campus_id))


DT::datatable(changec_10_test_df)

```

Now we write the function
```{r}
format_c_10 <- function(input_df) {
  
  output_df <- input_df %>%
    mutate(site_type = case_when(
    campus_id == "AC1" ~ 'A01',
    campus_id == "AU1" ~ 'A01',
    campus_id == "ACE" ~ 'A01',
    campus_id == "B8C" ~ 'B80',
    campus_id == "UOS" ~ 'C',
    campus_id == "OU1" ~ 'O01', #TODO should this be A01
    campus_id == "V01" ~ 'O01', #TODO should this be A01
    str_sub(campus_id, 1, 1) == 'C' ~ str_sub(campus_id, 1, 1),
    TRUE ~ campus_id))

output_df <- output_df %>% 
  select(course_reference_number, site_type)


return(output_df)
}
```
## Choose which data frame you want pass through the function 

 for the fake data set
```{r}
DT::datatable(format_c_10(c_10_test_df))
```

--- for the real data
```{r}
DT::datatable(format_c_10(real_c_10_df))
```
