---
title: "C-47 Course General Education Code"
author: "Craig Demke"
date: '2022-07-08'
output: html_document
---

```{r set global chunks, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE
)
```

```{r load libraries}
library(tidyverse)
library(datasets)
library(plotly)
library(gt)
library(glue)
library(stringr)
library(DT)
library(purrr)
library(here)
```
### This is part of the Course Data Element: C-47 
* ELEMENT NAME: General Education Course Codes 
* FIELD NAME: C_GEN_ED 
* FIELD FORMAT: Varchar, 4 Characters 
* DEFINITION: The codes which designate the required General Education requirements as  outlined in Regent Policy R470.  
Do NOT report courses beyond the Breadth General Education Requirements such as:  writing or quantitative intensive.


### This data is found in Edify from 
```{}

```


### Create fake data that matches this.

```{r}
c_47_course_gen_ed_code_test_df <- tibble(
  attribute_code = sample(c("EN", "SI", "ALUR", "ALCE", "LAB", "GC", "SS", "FA",
                            "HU", "ALCS", "PS", "OC", "MA", "FL", "LS", "ALCI",
                            "AI", "ALPP", "HON", "CP", "CS", "IL"), 10, replace = TRUE)
) 
   

DT::datatable(c_47_course_gen_ed_code_test_df, rownames=FALSE)
```

### Now let's see if we can pull in real data

```{r}
### We pull the data we want from the report database REPT 

c_47_course_gen_ed_code_real_df <- utHelpR::get_data_from_sql_file(file_name="c_47.sql",
                                               dsn="edify",
                                               context="sandbox")

# display data pulled in table
DT::datatable(c_47_course_gen_ed_code_real_df, rownames=FALSE)
```


### Here is the R script

The first thing I need to do is to figure out how to

```{r}

change_c_47_course_gen_ed_code_df <- c_47_course_gen_ed_code_test_df %>%
    mutate( c_gen_ed = case_when(
      attribute_code == "EN" ~ "C",
      attribute_code == "IL" ~ "IR",
      attribute_code == "CP" ~ "CL",
      attribute_code == "MA" ~ "QL",
      attribute_code == "QL" ~ attribute_code,
      attribute_code == "AI" ~ attribute_code,
      attribute_code == "FA" ~ attribute_code,
      attribute_code == "HU" ~ attribute_code,
      attribute_code == "SS" ~ attribute_code,
      attribute_code == "LS" ~ attribute_code,
      attribute_code == "PS" ~ attribute_code,
      attribute_code == "ID" ~ attribute_code,
      attribute_code == "IR" ~ attribute_code,
      attribute_code == "DV" ~ attribute_code,
      attribute_code == "CL" ~ attribute_code,
      attribute_code == "FL" ~ attribute_code,
      TRUE ~ "")) %>% 

    mutate( s_47 = c_gen_ed )
  

DT::datatable(change_c_47_course_gen_ed_code_df, rownames=FALSE)



```

### Making a function

```{r}
  
format_c_47_course_gen_ed_code <- function(input_df, with_intermediates=FALSE) {

  output_df <- input_df %>%
    mutate( c_gen_ed = case_when(
      attribute_code == "EN" ~ "C",
      attribute_code == "IL" ~ "IR",
      attribute_code == "CP" ~ "CL",
      attribute_code == "MA" ~ "QL",
      attribute_code == "QL" ~ attribute_code,
      attribute_code == "AI" ~ attribute_code,
      attribute_code == "FA" ~ attribute_code,
      attribute_code == "HU" ~ attribute_code,
      attribute_code == "SS" ~ attribute_code,
      attribute_code == "LS" ~ attribute_code,
      attribute_code == "PS" ~ attribute_code,
      attribute_code == "ID" ~ attribute_code,
      attribute_code == "IR" ~ attribute_code,
      attribute_code == "DV" ~ attribute_code,
      attribute_code == "CL" ~ attribute_code,
      attribute_code == "FL" ~ attribute_code,
      TRUE ~ "")) %>% 

    mutate( s_47 = c_gen_ed )
  

    if (!with_intermediates) {
      output_df <- output_df %>%
        select( -c(c_gen_ed) )
    }

  return(output_df)

  
}
```
### Choose which data frame you want pass through the function 

c_47_course_gen_ed_code_test_df for the fake data set
```{r}
DT::datatable(format_c_47_course_gen_ed_code(c_47_course_gen_ed_code_test_df), rownames=FALSE)
```

c_47_course_gen_ed_code_real_df for the real data
```{r}
DT::datatable(format_c_47_course_gen_ed_code(c_47_course_gen_ed_code_real_df), rownames=FALSE)
```

