---
title: "G-10 Degree Type"
author: "Craig Demke"
date: '2022-06-24'
output: html_document
---

```{r set global chunks, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE
)
```

```{r load libraries}
library(tidyverse)
library(datasets)
library(plotly)
library(gt)
library(glue)
library(stringr)
library(DT)
library(purrr)
library(here)
```
### This is part of the Graduation Data Element: G-10 
* ELEMENT NAME: Degree Type 
* FIELD NAME: G_DEG_TYPE 
* FIELD FORMAT: Varchar, 6 Characters 
* DEFINITION: The Level of Degree or Certificate Completed for the award conferred. Refer to the  Degree Type Table for all degrees. 


### This data is found in Edify from export.degrees_awarded, degree_ie and degree_status_code
```{}
SELECT DISTINCT (degree_id),
                degree_status_code
FROM degrees_awarded;
```


### Create fake data that matches the degree type in Edify

```{r}
g_10_degree_type_test_df <- tibble(
  degree_id = sample(c("AS", "BME", "MAT", "TR", "AB", "BAS", "BFA",
                              "CER1", "APE", "AC", "MA", "CER0", "AAS",
                              "BIS", "BSN", "MACC", "BA", "ND", "BM", "AA",
                              "MMFT", "BS"), 23, replace = TRUE),
  degree_status_code = sample(c("AW", "SO", "PN", "WD", "DN", ""), 23, replace = TRUE)
  
  
)
   

DT::datatable(g_10_degree_type_test_df, rownames=FALSE)
```

### Now let's see if we can pull in real data

```{r}
### We pull the data we want from the report database REPT 
library(here)
source(here::here("R", "data_io_util.R"))

g_10_degree_type_real_df <- get_data_from_sql_file(file_name="g_10.sql",
                             dsn="edify")
# display data pulled in table
DT::datatable(g_10_degree_type_real_df, rownames=FALSE)
```


### Here is the R script

The first thing I need to do is to figure out how to filter out any degrees which have not been awarded

```{r}

change_g_10_degree_type_df <- g_10_degree_type_test_df %>%
   mutate(degree_type = case_when(
   degree_status_code == "AW" ~ degree_id,
   TRUE ~ ""))


DT::datatable(change_g_10_degree_type_df, rownames=FALSE)



```

### Making a function

```{r}

format_g_10_degree_type <- function(input_df) {
  
  output_df <- input_df %>%  
  mutate(degree_type = case_when(
  degree_status_code == "AW" ~ degree_id,
  TRUE ~ "not awarded"))
  
  output_df <- output_df %>% 
  select(degree_type) %>% 
    filter(degree_type != "not awarded")
  
  return(output_df)
  
}
```
### Choose which data frame you want pass through the function 

g_10_degree_type_test_df for the fake data set
```{r}
DT::datatable(format_g_10_degree_type(g_10_degree_type_test_df), rownames=FALSE)
```

g_10_degree_type_real_df for the real data
```{r}
DT::datatable(format_g_10_degree_type(g_10_degree_type_real_df), rownames=FALSE)
```

