---
title: "G-14 Total Accepted Hours from Other Sources"
author: "Craig Demke"
date: '2022-07-13'
output: html_document
---

```{r set global chunks, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE
)
```

```{r load libraries}
library(tidyverse)
library(datasets)
library(plotly)
library(gt)
library(glue)
library(stringr)
library(DT)
library(purrr)
library(here)
```
### This is part of the Graduation Data Element: G-14 
* ELEMENT NAME: Accepted Credit from Other Sources 
* FIELD NAME: G_HRS_OTHER 
* FIELD FORMAT: Numeric (4,1) 
* DEFINITION: Hours from AP credit, CLEP test, Language test, Challenge, Military, etc. Hours  should all be converted to semester hours. 


### This data is found in Edify from 
```{}

```


### Create fake data that matches this.

```{r}
g_14_total_hours_other_test_df <- tibble(
  total_cumulative_clep_credits_earned = sample(0:10, 10, replace = TRUE),
  total_cumulative_ap_credits_earned = sample(0:10, 10, replace = TRUE),
  transfer_cumulative_credits_attempted_other_sources = sample(0:10, 10, replace = TRUE)
)

DT::datatable(g_14_total_hours_other_test_df, rownames=FALSE)
```

### Now let's see if we can pull in real data

```{r}
### We pull the data we want from the report database REPT 

g_14_total_hours_other_real_df <- utHelpR::get_data_from_sql_file(file_name="g_14_total_hours_other.sql",
                                               dsn="edify",
                                               context="sandbox")

# display data pulled in table
DT::datatable(g_14_total_hours_other_real_df, rownames=FALSE)
```


### Here is the R script

The first thing I need to do is to figure out how to

```{r}

change_g_14_total_hours_other_df <- g_14_total_hours_other_test_df %>%
   mutate(g_hrs_other = total_cumulative_clep_credits_earned +
             transfer_cumulative_credits_attempted_other_sources +
             total_cumulative_ap_credits_earned )
  
DT::datatable(change_g_14_total_hours_other_df, rownames=FALSE)

```

### Making a function

```{r}
  
format_g_14_total_hours_other <- function(input_df, with_intermediates=FALSE) {

  output_df <- input_df %>%
   mutate(g_hrs_other = (total_cumulative_clep_credits_earned +
             transfer_cumulative_credits_attempted_other_sources +
             total_cumulative_ap_credits_earned)) %>% 
    mutate(g_14 = (g_hrs_other))

    if (!with_intermediates) {
      output_df <- output_df %>%
        select( -c(g_hrs_other))
    }

  return(output_df)

  
}
```
### Choose which data frame you want pass through the function 

g_14_total_hours_other_test_df for the fake data set
```{r}
DT::datatable(format_g_14_total_hours_other(g_14_total_hours_other_test_df), rownames=FALSE)
```

g_14_total_hours_other_real_df for the real data
```{r}
DT::datatable(format_g_14_total_hours_other(g_14_total_hours_other_real_df), rownames=FALSE)
```

