---
title: "G-15 Total Remedial Hours"
author: "Craig Demke"
date: '2022-07-13'
output: html_document
---

```{r set global chunks, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE
)
```

```{r load libraries}
library(tidyverse)
library(datasets)
library(plotly)
library(gt)
library(glue)
library(stringr)
library(DT)
library(purrr)
library(here)
```
### This is part of the Graduation Data Element: G-15 
* ELEMENT NAME: Remedial Hours 
* FIELD NAME: G_REMEDIAL_HRS 
* FIELD FORMAT: Numeric (4,1) 
* DEFINITION: Remedial Hours which are included in S-20. Hours should all be converted to  semester hours. Applies only to undergrad degrees; grad degrees should be 0 


### This data is found in Edify from 
```{}

```


### Create fake data that matches this.

```{r}
g_15_remedial_hrs_test_df <- tibble(
  total_remedial_hours = sample(0:10, 10, replace = TRUE),
  level_id = sample(c("UG", "00", "GR", ""), 10,  replace = TRUE)
)
   

DT::datatable(g_15_remedial_hrs_test_df, rownames=FALSE)
```

### Now let's see if we can pull in real data

```{r}
### We pull the data we want from the report database REPT 

g_15_remedial_hrs_real_df <- utHelpR::get_data_from_sql_file(file_name="g_15_remedial_hrs.sql",
                                               dsn="edify",
                                               context="sandbox")

# display data pulled in table
DT::datatable(g_15_remedial_hrs_real_df, rownames=FALSE)
```


### Here is the R script

The first thing I need to do is to figure out how to

```{r}

change_g_15_remedial_hrs_df <- g_15_remedial_hrs_test_df %>%
    mutate(g_remedial_hrs = ifelse(level_id == "GR", "0", total_remedial_hours))

DT::datatable(change_g_15_remedial_hrs_df, rownames=FALSE)
```

### Making a function

```{r}
  
format_g_15_remedial_hrs <- function(input_df, with_intermediates=FALSE) {

  output_df <- input_df %>%
    mutate(g_remedial_hrs = ifelse(level_id == "GR", "0", total_remedial_hours)) %>% 
    mutate(g_15 = (g_remedial_hrs))

    if (!with_intermediates) {
      output_df <- output_df %>%
        select( -c(g_remedial_hrs) )
    }

  return(output_df)

  
}
```
### Choose which data frame you want pass through the function 

g_15_remedial_hrs_test_df for the fake data set
```{r}
DT::datatable(format_g_15_remedial_hrs(g_15_remedial_hrs_test_df), rownames=FALSE)
```

g_15_remedial_hrs_real_df for the real data
```{r}
DT::datatable(format_g_15_remedial_hrs(g_15_remedial_hrs_real_df), rownames=FALSE)
```
