---
title: "G-22 Workforce Education Earned Contact  Hours"
author: "Craig Demke"
date: '2022-06-27'
output: html_document
---

```{r set global chunks, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE
)
```

```{r load libraries}
library(tidyverse)
library(datasets)
library(plotly)
library(gt)
library(glue)
library(stringr)
library(DT)
library(purrr)
library(here)
```
### This is part of the Graduation Data G-22 and G-23

* This both of these should be 0 zero for Utah Tech

### This data is not found in Edify 
```{}

```


### Create fake data to hard code zero 0, I just used the student id as a data point

```{r}
g_22_workforce_ed_earned_contact_hours_test_df <- tibble(
  student_id = sample(1:999999, 10),
) %>% 
    mutate(student_id = str_pad(student_id, 8, pad = '0'))
   

DT::datatable(g_22_workforce_ed_earned_contact_hours_test_df, rownames=FALSE)
```

### Now let's see if we can pull in real data

```{r}
### We pull the data we want from the report database REPT 
library(here)
source(here::here("R", "data_io_util.R"))

g_22_workforce_ed_earned_contact_hours_real_df <- get_data_from_sql_file(file_name="g_21.sql",
                             dsn="edify")
# display data pulled in table
DT::datatable(g_22_workforce_ed_earned_contact_hours_real_df, rownames=FALSE)
```


### Here is the R script

The first thing I need to do is to figure out how hard code a zero. If the student id is the student id then 0

```{r}

change_g_22_workforce_ed_earned_contact_hours_df <- g_22_workforce_ed_earned_contact_hours_test_df %>%
   mutate(G_WE_EARNED_CONTACT_HRS = case_when(
     student_id == student_id ~ "0",
   TRUE ~ "error")) %>% 
  mutate(G_WE_PROGRAM_HRS = case_when(
     student_id == student_id ~ "0",
   TRUE ~ "error"))
  


DT::datatable(change_g_22_workforce_ed_earned_contact_hours_df, rownames=FALSE)



```

### Making a function

```{r}

format_g_22_workforce_ed_earned_contact_hours <- function(input_df) {
  
  output_df <- input_df %>%  
    mutate(G_WE_EARNED_CONTACT_HRS = case_when(
     student_id == student_id ~ "0",
   TRUE ~ "error")) %>% 
  mutate(G_WE_PROGRAM_HRS = case_when(
     student_id == student_id ~ "0",
   TRUE ~ "error"))
  
  output_df <- output_df %>% 
  select(G_WE_EARNED_CONTACT_HRS, G_WE_PROGRAM_HRS)
  
  return(output_df)
  
}
```
### Choose which data frame you want pass through the function 

g_22_workforce_ed_earned_contact_hours_test_df for the fake data set
```{r}
DT::datatable(format_g_22_workforce_ed_earned_contact_hours(g_22_workforce_ed_earned_contact_hours_test_df), rownames=FALSE)
```

g_22_workforce_ed_earned_contact_hours_real_df for the real data
```{r}
DT::datatable(format_g_22_workforce_ed_earned_contact_hours(g_22_workforce_ed_earned_contact_hours_real_df), rownames=FALSE)
```
