---
title: "G-21 Institutionally Assigned ID"
author: "Craig Demke"
date: '2022-06-27'
output: html_document
---
```{r set global chunks, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE
)
```

```{r load libraries}
library(tidyverse)
library(datasets)
library(plotly)
library(gt)
library(glue)
library(stringr)
library(DT)
library(purrr)
library(here)
```
### This is part of the Graduation Data Element: G-21 
*  ELEMENT NAME: Institutionally Assigned ID 
* FIELD NAME: G_BANNER_ID 
* FIELD FORMAT: Varchar, 9 Characters 
* DEFINITION: The unique institutionally assigned identification number for each student intended to  be used in lieu of using a student’s social security number. G_Banner_ID must begin with an Alpha  character representing the institution  


### This data is found in Edify from export.student, student_id 
```{}
SELECT student_id
FROM export.student
LIMIT 10;
```


### Create fake data that matches the ipeds_award_level_code data in Edify

```{r}
g_21_institutional_assigned_id_test_df <- tibble(
  student_id = sample(1:999999, 10),
) %>% 
    mutate(student_id = str_pad(student_id, 8, pad = '0'))
   

DT::datatable(g_21_institutional_assigned_id_test_df, rownames=FALSE)
```

### Now let's see if we can pull in real data

```{r}
### We pull the data we want from the report database REPT 

g_21_institutional_assigned_id_real_df <- utHelpR::get_data_from_sql_file(file_name="g_21.sql",
                                               dsn="edify",
                                               context="sandbox")
# display data pulled in table
DT::datatable(g_21_institutional_assigned_id_real_df, rownames=FALSE)
```


### Here is the R script

The first thing I need to do is to figure out how to

```{r}

change_g_21_institutional_assigned_id_df <- g_21_institutional_assigned_id_test_df %>% 
mutate(institutional_assigned_id = paste("D", student_id, sep = ""))

DT::datatable(change_g_21_institutional_assigned_id_df)

```

### Making a function

```{r}

format_g_21_institutional_assigned_id <- function(input_df) {
  
  output_df <- input_df %>%  
 mutate(institutional_assigned_id = paste("D", student_id, sep = ""))
  
  output_df <- output_df %>% 
  select(institutional_assigned_id)
  
  return(output_df)
  
}
```
### Choose which data frame you want pass through the function 

g_21_institutional_assigned_id_test_df for the fake data set
```{r}
DT::datatable(format_g_21_institutional_assigned_id(g_21_institutional_assigned_id_test_df), rownames=FALSE)
```

g_21_institutional_assigned_id_real_df for the real data
```{r}
DT::datatable(format_g_21_institutional_assigned_id(g_21_institutional_assigned_id_real_df), rownames=FALSE)
```

