---
title: "S_04_student_id_flag"
author: "Craig Demke"
date: '2022-06-22'
output: html_document
---

title: "s_04_student_id_flag"
output: html_document
date: '2022-06-01'
---

```{r set global chunks, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE
)
```

```{r load libraries}
library(tidyverse)
library(datasets)
library(plotly)
library(gt)
library(glue)
library(stringr)
library(DT)
library(purrr)
library(here)
```
## This is part of the Student Data This includes S-03 
* ELEMENT NAME: Student ID 
* FIELD NAME: S_ID 
* FIELD FORMAT: Varchar, 9 Characters 
* DEFINITION: Unique Identifier for enrolled student. Social Security Number shall be used (to  facilitate student tracking) except in the rare case where the student does not have SSN (i.e. international  student) where an institutionally defined number is used. 

## This is part of the Student Data This includes  S-04 
* ELEMENT NAME: Student ID Flag 
* FIELD NAME: S_ID_FLAG 
* FIELD FORMAT: Varchar, 1 Character 
* DEFINITION: Flag indicating if Student ID is the student's actual Social Security Number or an  institutionally assigned ID number (to identify students who don't have SSN's, i.e. International  Students). 

## This data is found in Edify from 
```{}
SELECT student_id,
       ssn
FROM student;
```


### Create fake data that matches this.

```{r}
s_04_student_id_flag_test_df <- tibble(
  student_id = sample(1:999999, 10),
  ssn = sample(c("123-45-678", ""), 10, replace = TRUE)) %>% 
    mutate(student_id = str_pad(student_id, 8, pad = '0'))
   
DT::datatable(s_04_student_id_flag_test_df, rownames=FALSE)
```

### Now let's see if we can pull in real data

```{r}
### We pull the data we want from the report database REPT 

s_04_student_id_flag_real_df <- utHelpR::get_data_from_sql_file(file_name="s_04.sql",
                                               dsn="edify",
                                               context="sandbox")
# display data pulled in table
DT::datatable(s_04_student_id_flag_real_df, rownames=FALSE)
```


## Here is the R script

The first thing I need to do is to figure out how to

```{r}

change_s_04_student_id_flag_df <- s_04_student_id_flag_test_df %>%
  mutate(student_id = paste("D", student_id, sep = ""))  %>% 
  mutate(s_id = case_when(
     ssn == "" ~ student_id,
     TRUE ~ ssn)) %>% 
    mutate(student_id_flag = case_when(
      s_id == student_id ~ 'I',
      TRUE ~ 'S'))


DT::datatable(change_s_04_student_id_flag_df, rownames=FALSE)



```

## Making a function

```{r}

format_s_04_student_id_flag <- function(input_df) {
  
  output_df <- input_df %>% 
  mutate(student_id = paste("D", student_id, sep = ""))  %>% 
  mutate(s_id = case_when(
     ssn == "" ~ student_id,
     TRUE ~ ssn)) %>% 
    mutate(student_id_flag = case_when(
      s_id == student_id ~ 'I',
      TRUE ~ 'S'))
 
  output_df <- output_df %>% 
  #select(s_id, student_id_flag)
  
  return(output_df)
  
}
```
## Choose which data frame you want pass through the function 

s_04_student_id_flag_test_df for the fake data set
```{r}
DT::datatable(format_s_04_student_id_flag(s_04_student_id_flag_test_df), rownames=FALSE)
```

s_04_student_id_flag_real_df for the real data
```{r}
DT::datatable(format_s_04_student_id_flag(s_04_student_id_flag_real_df), rownames=FALSE)
```
