---
title: "S-08 Current Zip Code"
author: "Craig Demke"
date: '2022-07-06'
output: html_document
---

```{r set global chunks, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE
)
```

```{r load libraries}
library(tidyverse)
library(datasets)
library(plotly)
library(gt)
library(glue)
library(stringr)
library(DT)
library(purrr)
library(here)
```
### This is part of the Students Data Element: S-08 
* ELEMENT NAME: Current Zip Code 
* FIELD NAME: S_CURR_ZIP 
* FIELD FORMAT: Varchar, 10 Characters 
* DEFINITION: The postal code of the student's current local address while attending classes. 


### This data is found in Edify from export.student, local_address_zip_code and ailing_address_zip_code
```{}
SELECT local_address_zip_code,
       mailing_address_zip_code
FROM student
```


### Create fake data that matches this.

```{r}
s_08_current_zip_code_test_df <- tibble(
  local_address_zip_code = sample(c("123456-7890", ""), 10, replace = TRUE),
   mailing_address_zip_code = sample(c("987654-3210", ""), 10, replace = TRUE)
)
  s_08_current_zip_code_test_df <- s_08_current_zip_code_test_df %>% 
    select(local_address_zip_code, mailing_address_zip_code )
DT::datatable(s_08_current_zip_code_test_df, rownames=FALSE)
```

### Now let's see if we can pull in real data

```{r}
### We pull the data from Edify

s_08_current_zip_code_real_df <- utHelpR::get_data_from_sql_file(file_name="s_08.sql",
                                               dsn="edify",
                                               context="sandbox")

# display data pulled in table
DT::datatable(s_08_current_zip_code_real_df, rownames=FALSE)
```


### Here is the R script

The first thing I need to do is to figure out how to

```{r}
change_s_08_current_zip_code_df <- s_08_current_zip_code_test_df %>%
  mutate(current_zip_code = case_when(
    local_address_zip_code != "" ~ local_address_zip_code,
    local_address_zip_code == "" ~ mailing_address_zip_code,
    mailing_address_zip_code != "" ~ mailing_address_zip_code, 
    TRUE ~ "000000"))
DT::datatable(change_s_08_current_zip_code_df, rownames=FALSE)
```

### Making a function

```{r}
format_s_08_current_zip_code <- function(input_df) {
  
  output_df <- input_df %>%  
   mutate(current_zip_code = case_when(
    local_address_zip_code != "" ~ local_address_zip_code,
    local_address_zip_code == "" ~ mailing_address_zip_code,
    mailing_address_zip_code != "" ~ mailing_address_zip_code, 
    TRUE ~ "000000"))
                                    
  
  #output_df <- output_df %>% 
  #select(current_zip_code)
  
  return(output_df)
  
}
```
### Choose which data frame you want pass through the function 

s_08_current_zip_code_test_df for the fake data set
```{r}
DT::datatable(format_s_08_current_zip_code(s_08_current_zip_code_test_df), rownames=FALSE)
```

s_08_current_zip_code_real_df for the real data
```{r}
DT::datatable(format_s_08_current_zip_code(s_08_current_zip_code_real_df), rownames=FALSE)
```
