---
title: "S-09 Citizenship Status"
author: "Craig Demke"
date: '2022-07-06'
output: html_document
---

```{r set global chunks, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE
)
```

```{r load libraries}
library(tidyverse)
library(datasets)
library(plotly)
library(gt)
library(glue)
library(stringr)
library(DT)
library(purrr)
library(here)
```
### This is part of the Student Data Element: S-09 
* ELEMENT NAME: Citizenship Status 
* FIELD NAME: S_CITZ_CODE 
* FIELD FORMAT: Varchar, 1 Character 
* DEFINITION: Indicates student's current citizenship status. 

### This data is found in Edify from export.student, us_citizenship_code
```{}
SELECT us_citizenship_code
FROM student;
```


### Create fake data that matches this.

```{r}
s_09_citizenship_status_test_df <- tibble(
  us_citizenship_code = sample(c("1", "2", "3", "4", "5", "6", "9", ""),23, replace = TRUE)
)
   
DT::datatable(s_09_citizenship_status_test_df, rownames=FALSE)
```

### Now let's see if we can pull in real data

```{r}
### We pull the data we want from the report database REPT 

s_09_citizenship_status_real_df <- utHelpR::get_data_from_sql_file(file_name="s_09.sql",
                                               dsn="edify",
                                               context="sandbox")
# display data pulled in table
DT::datatable(s_09_citizenship_status_real_df, rownames=FALSE)
```


### Here is the R script

The first thing I need to do is to figure out how to change 6 to 9 and what to do with null values

```{r}
change_s_09_citizenship_status_df <- s_09_citizenship_status_test_df %>%
    mutate(S_CITZ_CODE = case_when(
     us_citizenship_code == "6" ~ "9",
     us_citizenship_code == "" ~ "error",
     TRUE ~ us_citizenship_code))
     
DT::datatable(change_s_09_citizenship_status_df, rownames=FALSE)
```

### Making a function

```{r}
format_s_09_citizenship_status <- function(input_df) {
  
  output_df <- input_df %>%  
    mutate(S_CITZ_CODE = case_when(
     us_citizenship_code == "6" ~ "9",
     us_citizenship_code == "" ~ "error",
     TRUE ~ us_citizenship_code))
  
  #output_df <- output_df %>% 
  #select(S_CITZ_CODE)
  
  return(output_df)
  
}
```
### Choose which data frame you want pass through the function 

s_09_citizenship_status_test_df for the fake data set
```{r}
DT::datatable(format_s_09_citizenship_status(s_09_citizenship_status_test_df), rownames=FALSE)
```

s_09_citizenship_status_real_df for the real data
```{r}
DT::datatable(format_s_09_citizenship_status(s_09_citizenship_status_real_df), rownames=FALSE)
```
