---
title: "S-14 Ethnic Origin "
output: html_document
date: '2022-06-01'
---

```{r set global chunks, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE
)
```

```{r load libraries}
library(tidyverse)
library(datasets)
library(plotly)
library(gt)
library(glue)
library(stringr)
library(DT)
library(purrr)
library(here)
```
### This is part of the Student Data Submission to USHE Element S-14
* ELEMENT NAME: Ethnic Origin 
* FIELD NAME: S_ETHNIC 
* FIELD FORMAT: Varchar, 8 Characters,  
* DEFINITION: The racial and ethnic categories used to classify students.

### This data is found in Edify from export.student table
```{}
SELECT s.student_id,
       s.is_hispanic_latino_ethnicity,
       s.is_asian,
       s.is_black,
       s.is_american_indian_alaskan,
       s.is_hawaiian_pacific_islander,
       s.is_white,
       s.is_international,
       s.is_other_race
FROM export.student s;
```


### Create fake data that matches this.

```{r}
s_14_ethnic_origin_test_df <- tibble(
  student_id = sample(1:999999, 10),
  is_hispanic_latino_ethnicity = sample(c(TRUE, FALSE), 10, replace = TRUE),
  is_asian = sample(c(TRUE, FALSE), 10, replace = TRUE),
  is_black = sample(c(TRUE, FALSE), 10, replace = TRUE),
  is_american_indian_alaskan = sample(c(TRUE, FALSE), 10, replace = TRUE),
  is_hawaiian_pacific_islander = sample(c(TRUE, FALSE), 10, replace = TRUE),
  is_white = sample(c(TRUE, FALSE), 10, replace = TRUE),
  is_international = sample(c(TRUE, FALSE), 10, replace = TRUE),
  is_other_race = sample(c(TRUE, FALSE), 10, replace = TRUE)
) %>% 
    mutate(student_id = str_pad(student_id, 8, pad = '0'))

DT::datatable(s_14_ethnic_origin_test_df)
```

### Now let's see if we can pull in real data

```{r}
### We pull the data we want from the report database REPT 

s_14_ethnic_origin_test_real_df <- utHelpR::get_data_from_sql_file(file_name="s_14.sql",
                                                                   dsn="edify",
                                                                   context="sandbox")
# display data pulled in table
DT::datatable(s_14_ethnic_origin_test_real_df, rownames=FALSE)
```


## Here is the R script

The first thing I need to do is to figure out how to turn a true into a letter and false into a space. We use a case_when statement to changes the boolean logic of true or false into the USHE race field value. example: If is_hispanic_latino_ethnicity is coded as TRUE then there will be a new variable called "H" in the column called H

```{r}

change_s_14_ethnic_origin_df <- s_14_ethnic_origin_test_df %>%  
  mutate(H = case_when(
    is_hispanic_latino_ethnicity == TRUE ~ "H",
    is_hispanic_latino_ethnicity == FALSE ~ " ",
    TRUE ~ " ")) %>% 
  mutate(A = case_when(
    is_asian == TRUE ~ "A",
    is_asian == FALSE ~ " ",
    TRUE ~ " ")) %>%
  mutate(B = case_when(
    is_black ==  TRUE ~ "B",
    is_black == FALSE ~ " ",
    TRUE ~ " ")) %>%
  mutate(I = case_when(
    is_american_indian_alaskan == TRUE ~ "I",
    is_american_indian_alaskan == FALSE ~ " ",
    TRUE ~ " ")) %>%
  mutate(P = case_when(
    is_hawaiian_pacific_islander == TRUE ~ "P",
    is_hawaiian_pacific_islander == FALSE ~ " ",
    TRUE ~ " ")) %>%
  mutate(W = case_when(
    is_white == TRUE ~ "W",
    is_white == FALSE ~ " ",
    TRUE ~ " ")) %>%
  mutate(N = case_when(
    is_international == TRUE ~ "N",
    is_international == FALSE ~ " ",
    TRUE ~ " ")) %>%
  mutate(U = case_when(
    is_other_race == TRUE ~ "U",
    is_other_race == FALSE ~ " ",
    TRUE ~ " ")) # here I took out "mistake" and just put in a space because it was NA

change_s_14_ethnic_origin_df$"ethnic_origin" = paste(change_s_14_ethnic_origin_df$H, 
                                            change_s_14_ethnic_origin_df$A, 
                                            change_s_14_ethnic_origin_df$B,
                                            change_s_14_ethnic_origin_df$I,
                                            change_s_14_ethnic_origin_df$P, 
                                            change_s_14_ethnic_origin_df$W,
                                            change_s_14_ethnic_origin_df$N, 
                                            change_s_14_ethnic_origin_df$U,
                                            sep = "")

DT::datatable(change_s_14_ethnic_origin_df)

```


## Making a function

```{r}

format_s_14_ethnic_origin_df <- function(input_df) {
  
  output_df <- input_df %>%  
  mutate(H = case_when(
    is_hispanic_latino_ethnicity == TRUE ~ "H",
    is_hispanic_latino_ethnicity == FALSE ~ " ",
    TRUE ~ " ")) %>% 
  mutate(A = case_when(
    is_asian == TRUE ~ "A",
    is_asian == FALSE ~ " ",
    TRUE ~ " ")) %>%
  mutate(B = case_when(
    is_black ==  TRUE ~ "B",
    is_black == FALSE ~ " ",
    TRUE ~ " ")) %>%
  mutate(I = case_when(
    is_american_indian_alaskan == TRUE ~ "I",
    is_american_indian_alaskan == FALSE ~ " ",
    TRUE ~ " ")) %>%
  mutate(P = case_when(
    is_hawaiian_pacific_islander == TRUE ~ "P",
    is_hawaiian_pacific_islander == FALSE ~ " ",
    TRUE ~ " ")) %>%
  mutate(W = case_when(
    is_white == TRUE ~ "W",
    is_white == FALSE ~ " ",
    TRUE ~ " ")) %>%
  mutate(N = case_when(
    is_international == TRUE ~ "N",
    is_international == FALSE ~ " ",
    TRUE ~ " ")) %>%
  mutate(U = case_when(
    is_other_race == TRUE ~ "U",
    is_other_race == FALSE ~ " ",
    TRUE ~ " ")) 

  output_df$"ethnic_origin" = paste(output_df$H, output_df$A, output_df$B,
                                    output_df$I, output_df$P, output_df$W,
                                    output_df$N, output_df$U, sep = "")
  
  output_df <- output_df %>% 
    select(student_id, "ethnic_origin")
  
  return(output_df)
  
}
```
## Choose which data frame you want pass through the function 

s_14_ethnic_origin_test_df for the fake data set
```{r}
DT::datatable(format_s_14_ethnic_origin_df(s_14_ethnic_origin_test_df))
```

s_14_ethnic_origin_test_real_df for the real data
```{r}
DT::datatable(format_s_14_ethnic_origin_df(s_14_ethnic_origin_test_real_df))
```

