---
title: "S-17 Registration Status"
author: "Craig Demke"
date: '2022-06-23'
output: html_document
---

```{r set global chunks, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE
)
```

```{r load libraries}
library(tidyverse)
library(datasets)
library(plotly)
library(gt)
library(glue)
library(stringr)
library(DT)
library(purrr)
library(here)
library(lubridate)
```
### This is part of the Students Data Element: S-17
* ELEMENT NAME: Registration Status 
* FIELD NAME: S_REG_STATUS 
* FIELD FORMAT: Varchar, 2 Characters,  
* DEFINITION: Student's entry status at the beginning of the term.

### This data is found in Edify from expoert.student_term_level, student_type_code
```{}
--S-17
SELECT student_type_code
FROM student_term_level;
```


### Create fake data that matches this.

```{r}
s_17_registration_status_test_df <- tibble(
  student_type_code = sample(c("3", "S", "2", "R", "5", "N", "C", "0", "P", "H", "1", "F", "T"), 10, replace = FALSE),
  graduation_date_year = sample(2015:2022, 10, replace = TRUE),
  graduation_date_month = sample(01:12, 10, replace = TRUE),
  graduation_date_day = sample(01:29, 10, replace = TRUE),
  term_start_date = sample("2022-01-10", 10, replace = TRUE)) %>% 
  mutate(graduation_date_month = str_pad(graduation_date_month, 2, pad = '0')) %>% 
  mutate(graduation_date_day = str_pad(graduation_date_day, 2, pad = '0')) %>% 
  mutate(high_school_graduation_date = paste0(graduation_date_year, graduation_date_month, graduation_date_day)) 
  
 s_17_registration_status_test_df <- s_17_registration_status_test_df %>% 
  mutate(high_school_graduation_date = as_date(high_school_graduation_date)) %>%
  mutate(term_start_date = as_date(term_start_date)) %>%
   select(student_type_code , high_school_graduation_date, term_start_date)
  

DT::datatable(s_17_registration_status_test_df, rownames=FALSE)
```

### Now let's see if we can pull in real data

```{r}
### We pull the data we want from the report database REPT 

s_17_registration_status_real_df <- utHelpR::get_data_from_sql_file(file_name="s_17.sql",
                                               dsn="edify",
                                               context="sandbox")
# display data pulled in table
DT::datatable(s_17_registration_status_real_df, rownames=FALSE)
```


### Here is the R script

The first thing I need to do is to figure out how to convert Utah Tech student_type_code to USHE s_reg_status. I used the banner validation table to see what our codes were. 

```{}
SELECT stvstyp_code,
       stvstyp_desc
FROM banner.stvstyp;
```

Here is the R script
```{r}

change_s_17_registration_status_df <- s_17_registration_status_test_df %>%
      mutate(high_school_graduation_date = gsub("-", "", high_school_graduation_date)) %>% 
      mutate(term_start_date = gsub("-", "", term_start_date)) %>%
      mutate(high_school_graduation_date = as.numeric(high_school_graduation_date)) %>%
      mutate(term_start_date = as.numeric(term_start_date)) %>% 
      mutate(student_type_code2 = if_else(student_type_code == "F" & is.na(high_school_graduation_date) == TRUE, "FF",
                                          if_else(student_type_code == "F" & high_school_graduation_date + 10000 >= term_start_date, "FH",
                                                  if_else(student_type_code == "F" & 
                                                    high_school_graduation_date + 10000 <= term_start_date,"FF",
                                                          student_type_code)))) %>%  
      mutate(s_reg_status = case_when(
        student_type_code == "1" ~ 'NG', # New Graduate
        student_type_code == "2" ~ 'TG', # Transfer Graduate
        student_type_code == "3" ~ 'RG', # Readmit Graduate
        student_type_code == "5" ~ 'CG', # Continuing Graduate
        student_type_code == "C" ~ 'CS', # Continuing Registration
        student_type_code == "H" ~ 'HS', # High School
        student_type_code == "P" ~ 'CE', # Personal Interest, Non-Degree
        student_type_code == "R" ~ 'RS', # Readmit
        student_type_code == "T" ~ 'TU', # Transfer
        TRUE ~ student_type_code2))
  
DT::datatable(change_s_17_registration_status_df, rownames=FALSE)



```

### Making a function

```{r}

format_s_17_registration_status <- function(input_df, with_intermediates=FALSE) {
  
  output_df <- input_df %>%  
      mutate(high_school_graduation_date = gsub("-", "", high_school_graduation_date)) %>% 
      mutate(term_start_date = gsub("-", "", term_start_date)) %>%
      mutate(high_school_graduation_date = as.numeric(high_school_graduation_date)) %>%
      mutate(term_start_date = as.numeric(term_start_date)) %>% 
      mutate(student_type_code2 = if_else(student_type_code == "F" & is.na(high_school_graduation_date) == TRUE, "FF",
                                          if_else(student_type_code == "F" & high_school_graduation_date + 10000 >= term_start_date, "FH",
                                                  if_else(student_type_code == "F" & 
                                                    high_school_graduation_date + 10000 <= term_start_date,"FF",
                                                          student_type_code)))) %>%  
      mutate(s_reg_status = case_when(
        student_type_code == "1" ~ 'NG', # New Graduate
        student_type_code == "2" ~ 'TG', # Transfer Graduate
        student_type_code == "3" ~ 'RG', # Readmit Graduate
        student_type_code == "5" ~ 'CG', # Continuing Graduate
        student_type_code == "C" ~ 'CS', # Continuing Registration
        student_type_code == "H" ~ 'HS', # High School
        student_type_code == "P" ~ 'CE', # Personal Interest, Non-Degree
        student_type_code == "R" ~ 'RS', # Readmit
        student_type_code == "T" ~ 'TU', # Transfer
        TRUE ~ student_type_code2)) %>% 
    mutate(s_17 = (s_reg_status))
   
    if (!with_intermediates) {
      output_df <- output_df %>%
        select( -c(s_reg_status))
    }
  return(output_df)
  
}
```
### Choose which data frame you want pass through the function 

s_17_registration_status_test_df for the fake data set
```{r}
DT::datatable(format_s_17_registration_status(s_17_registration_status_test_df), rownames=FALSE)
```

s_17_registration_status_real_df for the real data
```{r}
DT::datatable(format_s_17_registration_status(s_17_registration_status_real_df), rownames=FALSE)
```
