---
title: "S-19 Degree Intent"
author: "Craig Demke"
date: '2022-06-24'
output: html_document
---

```{r set global chunks, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE
)
```

```{r load libraries}
library(tidyverse)
library(datasets)
library(plotly)
library(gt)
library(glue)
library(stringr)
library(DT)
library(purrr)
library(here)
```
### This is part of the Students Data Element: S-19
* ELEMENT NAME: Degree Intent 
* FIELD NAME: S_DEG_INTENT 
* FIELD FORMAT: Varchar, 2 Character 
* DEFINITION: The length/nature of the degree that the student is working toward. S_DEG_INTENT  with S_CURR_CIP represents the student’s major and ties to S_MAJOR

### This data is found in Edify from export.student_term_level, primary_degree_id
```{}
SELECT DISTINCT (primary_degree_id),
                primary_degree_desc
FROM student_term_level;
```


### Create fake data that matches the primary_degree_id in Edify.

```{r}
s_19_degree_intent_test_df <- tibble(
 primary_degree_id = sample(c("AS", "BME", "MAT", "TR", "AB", "BAS", "BFA",
                              "CER1", "APE", "AC", "MA", "CER0", "AAS",
                              "BIS", "", "BSN", "MACC", "BA", "ND", "BM", "AA",
                              "MMFT", "BS"), 23, replace = TRUE)
                            ) 
   

DT::datatable(s_19_degree_intent_test_df, rownames=FALSE)
```

### Now let's see if we can pull in real data

```{r}
### We pull the data we want from the report database REPT 
library(here)
source(here::here("R", "data_io_util.R"))

s_19_degree_intent_real_df <- get_data_from_sql_file(file_name="s_19.sql",
                             dsn="edify")
# display data pulled in table
DT::datatable(s_19_degree_intent_real_df, rownames=FALSE)
```


### Here is the R script

The first thing I need to do is to figure out how to

```{r}

change_s_19_degree_intent_df <- s_19_degree_intent_test_df %>%
   mutate(degree_intent = case_when(
     primary_degree_id == "AS" ~ '3',
     primary_degree_id == "BME" ~ '5',
     primary_degree_id == "MAT" ~ '7',
     primary_degree_id == "TR" ~ '0', #?
     primary_degree_id == "AB" ~ '3',
     primary_degree_id == "MAT" ~ '7',
     primary_degree_id == "BAS" ~ '5',
     primary_degree_id == "BFA" ~ '5',
     primary_degree_id == "CER1" ~ '?', #?
     primary_degree_id == "APE" ~ '3',
     primary_degree_id == "AC" ~ '3',
     primary_degree_id == "MA" ~ '7',
     primary_degree_id == "CER0" ~ '?', #?
     primary_degree_id == "AAS" ~ '3',
     primary_degree_id == "BIS" ~ '5',
     primary_degree_id == "" ~ '0', #?
     primary_degree_id == "BSN" ~ '5',
     primary_degree_id == "MACC" ~ '7',
     primary_degree_id == "BA" ~ '5',
     primary_degree_id == "ND" ~ '0', #?
     primary_degree_id == "BM" ~ '5',
     primary_degree_id == "AA" ~ '3',
     primary_degree_id == "MMFT" ~ '7',
     primary_degree_id == "BS" ~ '5',
     TRUE ~ "error"))
  


DT::datatable(change_s_19_degree_intent_df, rownames=FALSE)



```

### Making a function

```{r}

format_s_19_degree_intent <- function(input_df) {
  
  output_df <- input_df %>%  
 mutate(degree_intent = case_when(
     primary_degree_id == "AS" ~ '3',
     primary_degree_id == "BME" ~ '5',
     primary_degree_id == "MAT" ~ '7',
     primary_degree_id == "TR" ~ '0', #?
     primary_degree_id == "AB" ~ '3',
     primary_degree_id == "MAT" ~ '7',
     primary_degree_id == "BAS" ~ '5',
     primary_degree_id == "BFA" ~ '5',
     primary_degree_id == "CER1" ~ '?', #?
     primary_degree_id == "APE" ~ '3',
     primary_degree_id == "AC" ~ '3',
     primary_degree_id == "MA" ~ '7',
     primary_degree_id == "CER0" ~ '?', #?
     primary_degree_id == "AAS" ~ '3',
     primary_degree_id == "BIS" ~ '5',
     primary_degree_id == "" ~ '0', #?
     primary_degree_id == "BSN" ~ '5',
     primary_degree_id == "MACC" ~ '7',
     primary_degree_id == "BA" ~ '5',
     primary_degree_id == "ND" ~ '0', #?
     primary_degree_id == "BM" ~ '5',
     primary_degree_id == "AA" ~ '3',
     primary_degree_id == "MMFT" ~ '7',
     primary_degree_id == "BS" ~ '5',
     TRUE ~ "error"))
  
  #output_df <- output_df %>% 
  #select(degree_intent)
  
  return(output_df)
  
}
```
### Choose which data frame you want pass through the function 

s_19_degree_intent_test_df for the fake data set
```{r}
DT::datatable(format_s_19_degree_intent(s_19_degree_intent_test_df), rownames=FALSE)
```

s_19_degree_intent_real_df for the real data
```{r}
DT::datatable(format_s_19_degree_intent(s_19_degree_intent_real_df), rownames=FALSE)
```

