---
title: "S-23 Cumulative Institutional Graduate GPA"
author: "Craig Demke"
date: '2022-06-28'
output: html_document
---

```{r set global chunks, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE
)
```

```{r load libraries}
library(tidyverse)
library(datasets)
library(plotly)
library(gt)
library(glue)
library(stringr)
library(DT)
library(purrr)
library(here)
```
### This is part of the Students Data Element: S-23 
* ELEMENT NAME: Cumulative Institutional Graduate GPA 
* FIELD NAME: S_CUM_GPA_GRAD 
* FIELD FORMAT: Numeric (4,3) 
* DEFINITION: Student's Cumulative GPA as of the present academic term as a graduate student. All  credit hours should represent average course grade on a 4.0 scale. This GPA ties to earned credits in  Cumulative Institutional Graduate Hours. 

### This data is found in Edify from export.student_term_level, institutional_cumulative_gpa, level_id
```{}
SELECT institutional_cumulative_gpa,
       level_id
FROM student_term_level;
```


### Create fake data that matches this.

```{r}
s_23_cumulative_institutional_graduate_gpa_test_df <- tibble(
  institutional_cumulative_gpa = sample(0.0:4.0, 10, replace = TRUE),
  level_id = sample(c("UG", "NC", "GR", "CE", "00", ""), 10, replace = TRUE)
)
   
DT::datatable(s_23_cumulative_institutional_graduate_gpa_test_df, rownames=FALSE)
```

### Now let's see if we can pull in real data

```{r}
### We pull the data we want from the report database REPT 
library(here)
source(here::here("R", "data_io_util.R"))

s_23_cumulative_institutional_graduate_gpa_real_df <- get_data_from_sql_file(file_name="s_23.sql",
                             dsn="edify")
# display data pulled in table
DT::datatable(s_23_cumulative_institutional_graduate_gpa_real_df, rownames=FALSE)
```


### Here is the R script

The first thing I need to do is to figure out how to

```{r}

change_s_23_cumulative_institutional_graduate_gpa_df <- s_23_cumulative_institutional_graduate_gpa_test_df %>%
   mutate(cumulative_institutional_graduate_gpa = ifelse(level_id == "GR", round(institutional_cumulative_gpa, digits = 2), 0)
          )
  
DT::datatable(change_s_23_cumulative_institutional_graduate_gpa_df, rownames=FALSE)

```

### Making a function

```{r}

format_s_23_cumulative_institutional_graduate_gpa <- function(input_df) {
  
  output_df <- input_df %>%
     mutate(cumulative_institutional_graduate_gpa = ifelse(level_id == "GR", round(institutional_cumulative_gpa, digits = 2), 0)
          )
  
  #output_df <- output_df %>% 
  #select(cumulative_institutional_undergraduate_gpa)
  
  return(output_df)
  
}
```
### Choose which data frame you want pass through the function 

s_23_cumulative_institutional_graduate_gpa_test_df for the fake data set
```{r}
DT::datatable(format_s_23_cumulative_institutional_graduate_gpa(s_23_cumulative_institutional_graduate_gpa_test_df), rownames=FALSE)
```

s_23_cumulative_institutional_graduate_gpa_real_df for the real data
```{r}
DT::datatable(format_s_23_cumulative_institutional_graduate_gpa(s_23_cumulative_institutional_graduate_gpa_real_df), rownames=FALSE)
```
