---
title: "S-26 Age at 3rd Week"
author: "Craig Demke"
date: '2022-06-24'
output: html_document
---

```{r set global chunks, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE
)
```

```{r load libraries}
library(tidyverse)
library(datasets)
library(plotly)
library(gt)
library(glue)
library(stringr)
library(DT)
library(purrr)
library(here)
library(lubridate)
```
### This is part of the Students Data Element: S-26
* ELEMENT NAME: Age at 3rd Week 
* FIELD NAME: S_AGE 
* FIELD FORMAT: Numeric (3,0) 
* DEFINITION: The age of the student at third week extract date. 

### This data is found in Edify from export.student, birth_date and export.student_term_level_version, verson_date
```{}
SELECT s.birth_date,
       v.term_id,
       v.version_id,
       v.version_date
FROM student s
LEFT JOIN student_term_level_version v
ON s.student_id = v.student_id
WHERE version_id = '3'
AND term_id = '202220'
LIMIT 10;
```


### Create fake data that matches this.

```{r}
s_26_age_at_3rd_week_test_df <- tibble(
  version_date = as_date("2022-06-24"),
  birth_date_year = sample(1978:2010, 10, replace = TRUE),
  birth_date_month = sample(01:12, 10, replace = TRUE),
  birth_date_day = sample(01:29, 10, replace = TRUE)) %>% 
  mutate(birth_date_month = str_pad(birth_date_month, 2, pad = '0')) %>% 
  mutate(birth_date_day = str_pad(birth_date_day, 2, pad = '0')) 
  
  
 s_26_age_at_3rd_week_test_df$"birth_date" =
   paste(s_26_age_at_3rd_week_test_df$birth_date_year, 
         s_26_age_at_3rd_week_test_df$birth_date_month, 
         s_26_age_at_3rd_week_test_df$birth_date_day, sep = "-")

 s_26_age_at_3rd_week_test_df <- s_26_age_at_3rd_week_test_df %>%
  mutate(birth_date = as_date(birth_date)) %>% 
   select(birth_date, version_date)  

DT::datatable(s_26_age_at_3rd_week_test_df, rownames=FALSE)
```

### Now let's see if we can pull in real data

```{r}
### We pull the data we want from the report database REPT 
library(here)
source(here::here("R", "data_io_util.R"))

s_26_age_at_3rd_week_real_df <- get_data_from_sql_file(file_name="S_26.sql",
                             dsn="edify")
# display data pulled in table
DT::datatable(s_26_age_at_3rd_week_real_df, rownames=FALSE)
```


### Here is the R script

The first thing I need to do is to figure out how to

```{r}
age <- s_26_age_at_3rd_week_test_df %>% 
select(birth_date, version_date) %>% 
mutate(age = trunc((birth_date %--% version_date) / years(1)))

DT::datatable(age, rownames=FALSE)

```

### Making a function

```{r}

format_s_26_age_at_3rd_week <- function(input_df) {
  
  output_df <- input_df %>%  
  mutate(age = trunc((birth_date %--% version_date) / years(1))) %>% 
  #mutate(age = ifelse(age = "", 0, age)) # will this give a zerro for missing ages
  
 # output_df <- output_df %>% 
  #select(age)
  
  return(output_df)
  
}
```
### Choose which data frame you want pass through the function 

s_26_age_at_3rd_week_test_df for the fake data set
```{r}
DT::datatable(format_s_26_age_at_3rd_week(s_26_age_at_3rd_week_test_df), rownames=FALSE)
```

s_26_age_at_3rd_week_real_df for the real data
```{r}
DT::datatable(format_s_26_age_at_3rd_week(s_26_age_at_3rd_week_real_df), rownames=FALSE)
```

